---
title: "Management of duplicates in ris files"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
---


```{r setup}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 70), tidy = TRUE, cache=F)
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "footnotesize","\n\n", x, "\n\n \\normalsize\n\n")
})
```


# Extracting and analysing ris Files

## Creating the reading function
```{r file="./readRis.R"}
source("./readRis.R")
```

# Extracting fields

```{r file="./extractFields.R"}
source("./extractFields.R")
```

# Finding duplicates

In order to find duplicate when comparing ris files, we will use the following steps:

1. documents having the same doi will be tested for resemblance in their titles considered duplicates, if they are not chapters of a book, because those may be referenced with the DOI of the book...
2. documents not having a DOI will be compared (between them and with the ones having a doi) in terms of resemblance in their titles and years. If they have a very similar title and a maximum of one year difference, they will be considered as duplicates.

In order to compare titles:
1. we suppress all the characters which are not classical letters (space, punctuation, etc.)
1. we put every character in lower case
1. we compare strings

At first we used the following distance-based string comparation: String Alignment distance (restricted Damerau-Levenshtein distance), divide it by the length of the smallest string. Values inferior to 0.05 are considered identical, i.e. if less than 5\% of the characters of the smallest string must be added or modified to obtain the larger one, they are considered identical.
However, some obviously different documents were considered duplicates, so we now just consider exact matches in modified titles.
The result is that some of the duplicates are not found, but no false dupe is deleted.


Also note that if 2 documents have the same title and year but have different type, the articles and book chapters will have the priority over the conferences (for the duplicate which will be kept in the ris file).

## function definitions

### finding duplicates

```{r file="./duplicate_search_function.R"}
source("./duplicate_search_function.R")
```

### Modifying and writing ris objects

```{r file="./filterRis.R"}
source("./filterRis.R")
```

# Application

## Making one file out of multiple files
```{r}
dirProquest<-"../../Search/Results/proquest ana /"
fileProquest<-tempfile()
writeLines(unlist(lapply(paste0(dirProquest,dir(dirProquest,pattern="ris")),function(x)c(readLines(x),""))),con = fileProquest)

dirInformit<-"../../Search/Results/informit/"
fileInformit<-tempfile()
writeLines(unlist(lapply(paste0(dirInformit,dir(dirInformit,pattern="ris")),function(x)c(readLines(x),""))),con = fileInformit)

dirWosCore<-"../../Search/Results/wosCore20230503/"
fileWosCore<-tempfile()
writeLines(unlist(lapply(paste0(dirWosCore,dir(dirWosCore,pattern="ris")),function(x)c(readLines(x),""))),con = fileWosCore)


proquest<-read_ris(fileProquest,title="T1")
proquest<-synoFields(proquest)
informit<-read_ris(fileInformit,title="T1",multiLine="N2")
informit<-synoFields(informit)
wosCore<-read_ris(fileWosCore)
```

## Reading unique file

```{r}
ebsco <- read_ris("../../Search/Results/EbscoJames/620fd6a2-22fd-429e-aa34-9bd22d3fffed.ris",title = "T1")
ebsco <- synoFields(ebsco)
embase <- read_ris("../../Search/Results/Embase20230418/records.ris",title="T1",multiLine = "N2")
embase <-synoFields(embase,c("T1","N2","Y1","A1"),c("TI","AB","PY","AU"))
angel <- read_ris("../../Search/Results/angelGene20230502/angelgene.ris")
scopus <- read_ris("../../Search/Results/scopus20230503/scopus.ris")
wosScielo <- read_ris("../../Search/Results/wosSciELO20230503/savedrecs.ris")
```


## description

```{r}
dataList<-c("scopus","wosCore","wosScielo","embase","ebsco","proquest","informit","angel")
lapply(mget(dataList),function(x)table(x$fieldName))
lapply(mget(dataList),function(x)table(x$content[x$fieldName=="PY"]))
```



## Corrections on files
The functions to modify ris file objects in R are in [./modifyRis.R](./modifyRis.R)
```{r}
source("./modifyRis.R")
```

### Ebsco publications years

The "PY" field in the ebsco files is definitely not what it should:

```{r}
A<-extractFields(ebsco,c("PY","Y1"))
head(A,n=10)
any(!is.na(A$PY) & !is.na(A$Y1))

```

So what we will do is:

1. to move "PY" to the field "Y1"
1. extract the years from the new field "Y1"
1. add a field "PY" to put the years

```{r}
ebsco<-changeFieldName(ebsco,"PY","Y1",title="T1")
valPY<-gsub("^([0-9]{4})/.*","\\1",extractFields(ebsco,"Y1")$Y1)
ebsco <- addField(ebsco, fieldName = "PY",values = valPY)
```

```{r}
head(extractFields(ebsco,"PY")$PY)
```

### Class climate and classroom climate in Ebsco file
It appears that the filter of class climate and classroom climate did not work in the search, we will do it by hand here

```{r}
ebscoTS <- extractFields(ebsco,c("TI","AB","KW"))
toSupp <- ebscoTS[which(grepl("class climate",ebscoTS$TI)|grepl("classroom climate",ebscoTS$TI)|
grepl("class climate",ebscoTS$AB)|grepl("classroom climate",ebscoTS$AB)|
grepl("class climate",ebscoTS$KW)|grepl("classroom climate",ebscoTS$KW)),"id"]
ebsco <- filterRis(ebsco, toSupp)
```



## Finding and deleting internal duplicates in Ris Files

```{r}
intDupe_scopus <- risInternalDuplicate(scopus)
scopus <- filterRis(scopus,intDupe_scopus$toSupp)

intDupe_wosCore <- risInternalDuplicate(wosCore)
wosCore <- filterRis(wosCore,intDupe_wosCore$toSupp)

intDupe_wosScielo <- risInternalDuplicate(wosScielo)
wosScielo <- filterRis(wosScielo,intDupe_wosScielo$toSupp)

intDupe_ebsco <- risInternalDuplicate(ebsco)
ebsco <- filterRis(ebsco,intDupe_ebsco$toSupp)

intDupe_proquest <- risInternalDuplicate(proquest)
proquest <- filterRis(proquest,intDupe_proquest$toSupp)

intDupe_informit <- risInternalDuplicate(informit)
informit <- filterRis(informit,intDupe_informit$toSupp)

intDupe_embase <- risInternalDuplicate(embase)
embase <- filterRis(embase, intDupe_embase$toSupp)

angel# only one record... no 
```

```{r}
#for(i in 2:length(dataList))
#{
#  for(j in 1:(i-1))
#  {
#    cat(paste0("dupe_",dataList[i],"_",dataList[j]," <- #compareRisDuplicate(",dataList[i],", ",dataList[j],")\n",
#        dataList[i]," <- filterRis(",dataList[i],", dupe_",dataList[i],"_",dataList[j],"$toSupp)\n"))
#  }
#}

dupe_wosCore_scopus <- compareRisDuplicate(wosCore, scopus)
wosCore <- filterRis(wosCore, dupe_wosCore_scopus$toSupp)
dupe_wosScielo_scopus <- compareRisDuplicate(wosScielo, scopus)
wosScielo <- filterRis(wosScielo, dupe_wosScielo_scopus$toSupp)
dupe_wosScielo_wosCore <- compareRisDuplicate(wosScielo, wosCore)
wosScielo <- filterRis(wosScielo, dupe_wosScielo_wosCore$toSupp)
dupe_embase_scopus <- compareRisDuplicate(embase, scopus)
embase <- filterRis(embase, dupe_embase_scopus$toSupp)
dupe_embase_wosCore <- compareRisDuplicate(embase, wosCore)
embase <- filterRis(embase, dupe_embase_wosCore$toSupp)
dupe_embase_wosScielo <- compareRisDuplicate(embase, wosScielo)
embase <- filterRis(embase, dupe_embase_wosScielo$toSupp)
dupe_ebsco_scopus <- compareRisDuplicate(ebsco, scopus)
ebsco <- filterRis(ebsco, dupe_ebsco_scopus$toSupp)
dupe_ebsco_wosCore <- compareRisDuplicate(ebsco, wosCore)
ebsco <- filterRis(ebsco, dupe_ebsco_wosCore$toSupp)
dupe_ebsco_wosScielo <- compareRisDuplicate(ebsco, wosScielo)
ebsco <- filterRis(ebsco, dupe_ebsco_wosScielo$toSupp)
dupe_ebsco_embase <- compareRisDuplicate(ebsco, embase)
ebsco <- filterRis(ebsco, dupe_ebsco_embase$toSupp)
dupe_proquest_scopus <- compareRisDuplicate(proquest, scopus)
proquest <- filterRis(proquest, dupe_proquest_scopus$toSupp)
dupe_proquest_wosCore <- compareRisDuplicate(proquest, wosCore)
proquest <- filterRis(proquest, dupe_proquest_wosCore$toSupp)
dupe_proquest_wosScielo <- compareRisDuplicate(proquest, wosScielo)
proquest <- filterRis(proquest, dupe_proquest_wosScielo$toSupp)
dupe_proquest_embase <- compareRisDuplicate(proquest, embase)
proquest <- filterRis(proquest, dupe_proquest_embase$toSupp)
dupe_proquest_ebsco <- compareRisDuplicate(proquest, ebsco)
proquest <- filterRis(proquest, dupe_proquest_ebsco$toSupp)
dupe_informit_scopus <- compareRisDuplicate(informit, scopus)
informit <- filterRis(informit, dupe_informit_scopus$toSupp)
dupe_informit_wosCore <- compareRisDuplicate(informit, wosCore)
informit <- filterRis(informit, dupe_informit_wosCore$toSupp)
dupe_informit_wosScielo <- compareRisDuplicate(informit, wosScielo)
informit <- filterRis(informit, dupe_informit_wosScielo$toSupp)
dupe_informit_embase <- compareRisDuplicate(informit, embase)
informit <- filterRis(informit, dupe_informit_embase$toSupp)
dupe_informit_ebsco <- compareRisDuplicate(informit, ebsco)
informit <- filterRis(informit, dupe_informit_ebsco$toSupp)
#dupe_informit_proquest <- compareRisDuplicate(informit, proquest)
#informit <- filterRis(informit, dupe_informit_proquest$toSupp)
dupe_angel_scopus <- compareRisDuplicate(angel, scopus)
angel <- filterRis(angel, dupe_angel_scopus$toSupp)
dupe_angel_wosCore <- compareRisDuplicate(angel, wosCore)
angel <- filterRis(angel, dupe_angel_wosCore$toSupp)
dupe_angel_wosScielo <- compareRisDuplicate(angel, wosScielo)
angel <- filterRis(angel, dupe_angel_wosScielo$toSupp)
dupe_angel_embase <- compareRisDuplicate(angel, embase)
angel <- filterRis(angel, dupe_angel_embase$toSupp)
dupe_angel_ebsco <- compareRisDuplicate(angel, ebsco)
angel <- filterRis(angel, dupe_angel_ebsco$toSupp)
dupe_angel_proquest <- compareRisDuplicate(angel, proquest)
angel <- filterRis(angel, dupe_angel_proquest$toSupp)
dupe_angel_informit <- compareRisDuplicate(angel, informit)
angel <- filterRis(angel, dupe_angel_informit$toSupp)


```


# Writing final Ris files

```{r}
DIR <- "../../Search/finalRis/"
if(dir.exists(DIR))
{
  unlink(DIR,recursive=T)
}
dir.create(DIR)
for(i in 1:length(dataList))
{
  writeRis(get(dataList[i]),filename=paste0(DIR,dataList[i],".ris"))
}
```


