---
title: "Example of use of the assignment functions with the documents of the full text screening"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
---


# Reading source functions


```{r}
source("./docAssignment_functions.R")
```

# Creating the project

All the information we need to create the project is in the excel file with the document, that we will use as well to make the document reviews.

```{r}
require(openxlsx)
completeFTS <- read.xlsx("../../screening/fullTextScreening/fullTextScreening.xlsx")
listDocument <- data.frame(documents=completeFTS$abbrev,categ="default")
listDocument$categ[completeFTS$group%in%c("Thesis","thesis","Book")] <- "thesesOrBook"
listDocument$categ[!is.na(completeFTS$group)]
listDocument$categ[!completeFTS$pdfDownloaded]<-"missingPdf"
listDocument$categ[completeFTS$unclear]<-"unclear"
(documents<-tapply(listDocument$documents,listDocument$categ,function(x)x))
```

Then we create the project with the following function:

```r
createProj(
  name="FTS",
  documents=documents,
  people=c("Ana","Marius","Sara","Luisa","Sergio","Benjamin","JuanGabriel"),
  nameFile="FTS.RData",
  dirProject="../../screening/fullTextScreening/",
  nbReview_categ=c(default=2,missingPdf=2,thesesOrBook=2,unclear=2),
  priority=c("unclear","default","missingPdf","thesesOrBook")
)
```

We load the project that way:

```{r}
(load("../../screening/fullTextScreening/FTS.RData"))
```

# Making assignment by hand

Luisa told me that she already started reviewing the documents from the unclear section:

```r
FTS<-addManualAssignment(FTS,person="Luisa",documents=documents$unclear)
```

# Making automatic assignments

Sergio asked me 5 documents:

```r
FTS<-createAssigment_auto(FTS,nbDoc=5,person="Sergio")
```













# Current state


In the following table, you will see the current state of assigned document in the Full Text Screening project:

```{r}
require(knitr)
rt<-reviewTable(FTS)
kable(rt)
```

