---
title: "Reading the results of the assignments and extracting the interesting data (example of a full-text screening exercise)"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
---


In order to read the results of the assignments, we put all the resulting excel files in a unique directory:



```{r}
require(openxlsx)
dirResults <- "../../screening/fullTextScreening/DONE/"
patternFiles <- "^assignment([0-9]{1,4})_([A-Za-z]+)_([0-9]+)\\.xlsx$"
finalDecisionFile <- "FinalDecision.xlsx"
finalDecisionTab <- read.xlsx(paste(dirResults,finalDecisionFile,sep="/"))
sheetName <- "Sheet 1"
idDoc <- "abbrev"
(filesResults<-dir(dirResults,pattern=patternFiles))
assignment<-gsub(patternFiles,"\\1",filesResults)
person<-gsub(patternFiles,"\\2",filesResults)
dateAssign<-gsub(patternFiles,"\\3",filesResults)
listResults<-lapply(paste(dirResults,filesResults,sep="/"),read.xlsx,sheet=sheetName)
nameCol<-lapply(listResults,colnames)
unNameCol<-unique(unlist(nameCol))
docAnalysed<-data.frame(
  assignment=as.numeric(rep(assignment,sapply(listResults,nrow))),
  person=rep(person,sapply(listResults,nrow)),
  id=unlist(lapply(listResults,function(x,a)x[,a],a=idDoc)),
  inclusion=gsub("^ +","",gsub(" +$" ,"", unlist(lapply(listResults,function(x,a)x[,a],a="Inclusion")))),
  reasonExcl=unlist(lapply(listResults,function(x,a)x[,a],a="ReasonExlusion")),
  comment=unlist(lapply(listResults,function(x,a)x[,a],a="Comment"))
  
)

table(docAnalysed$inclusion)
docAnalysed$incl<-NA
docAnalysed$incl[docAnalysed$inclusion%in%c("1","TRUE")]<-T
docAnalysed$incl[docAnalysed$inclusion%in%c("0","FALSE")]<-F
table(docAnalysed$incl,useNA="ifany")
```
Which are the documents which were reviewed more than once:

```{r}
nbRev<-table(docAnalysed$id)
(moreThanOnce <- names(nbRev)[nbRev>1])
mTO_noFinalD <- moreThanOnce[!moreThanOnce%in%finalDecisionTab$abbrev]
conflictOnInclusion <- by(docAnalysed[docAnalysed$id%in%mTO_noFinalD,],docAnalysed$id[docAnalysed$id%in%mTO_noFinalD],function(tab)
  {
    any(is.na(tab$incl))|length(unique(tab$incl))>1
  },simplify = T)
(w_conflict_incl <- names(conflictOnInclusion)[conflictOnInclusion])
toTest_conflictReason<-mTO_noFinalD[!mTO_noFinalD%in%w_conflict_incl]
conflictOnReason <- by(docAnalysed[docAnalysed$id%in%toTest_conflictReason,],docAnalysed$id[docAnalysed$id%in%toTest_conflictReason],function(tab)
  {
    length(unique(tab$reasonExcl))>1
  },simplify=T)
(w_conflict_reason<-names(conflictOnReason)[conflictOnReason])
```

# Numbers


Number of article reviewed by more than one person:
```{r}
length(moreThanOnce)
```

Number of papers accepted without conflict:
```{r}
accepted <- by(docAnalysed[docAnalysed$id%in%moreThanOnce,],docAnalysed$id[docAnalysed$id%in%moreThanOnce],function(tab)
  {
    all(tab$incl)
  },simplify = T)
sum(na.omit(as.logical(accepted)))
```

Reason of exclusions when excluded without conflicts:
```{r}
exclusionReason <- by(docAnalysed[docAnalysed$id%in%moreThanOnce,],docAnalysed$id[docAnalysed$id%in%moreThanOnce],function(tab)
  {
    if(!any(is.na(tab$incl))&all(!tab$incl))
    {return(unique(tab$reasonExcl))}else
    {return(NA)}
  
  },simplify = T)
#exclusionReason
(reasonOK<-exclusionReason[sapply(exclusionReason,function(x)length(x)==1&!any(is.na(x)))])
```





# Conflicts

## Inclusion 

```{r results='asis'}
require(kableExtra)
for(i in w_conflict_incl)
{
  cat('### ',i,'\n\n')
  tab_toShow<-docAnalysed[docAnalysed$id==i,c("assignment","person","incl","reasonExcl","comment")]
  #tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50]<-paste(substr(tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50],1,46),"...")
  cat(kable(tab_toShow,format="html"))
  cat("\n\n")
}
```

## Reason of exclusion

```{r results='asis'}
require(kableExtra)
for(i in w_conflict_reason)
{
  cat('### ',i,'\n\n')
  tab_toShow<-docAnalysed[docAnalysed$id==i,c("assignment","person","incl","reasonExcl","comment")]
  #tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50]<-paste(substr(tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50],1,46),"...")
  cat(kable(tab_toShow,format="html"))
  cat("\n\n")
}
```


# Resolved conflicts

```{r results='asis'} 
resolved<-finalDecisionTab$abbrev
for(i in resolved)
{
  cat('## ',i,'\n\n')
  tab_toShow<-docAnalysed[docAnalysed$id==i,c("assignment","person","incl","reasonExcl","comment")]
  #tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50]<-paste(substr(tab_toShow$comment[!is.na(tab_toShow$comment)&nchar(tab_toShow$comment)>50],1,46),"...")
  cat(kable(tab_toShow,format="html"))
  cat("\n\n")
  cat("**Decision**:\n\n")
  cat(kable(finalDecisionTab[finalDecisionTab$abbrev==i,],format="html"))
  cat("\n\n")
}
```


# Final Numbers

```{r}
(AcceptedFinal <- c(names(accepted)[!is.na(as.logical(accepted))&as.logical(accepted)],
                   finalDecisionTab$abbrev[!is.na(finalDecisionTab$Inclusion)&as.logical(finalDecisionTab$Inclusion)]))

AcceptedFinal<-AcceptedFinal[!AcceptedFinal %in% finalDecisionTab$abbrev[!finalDecisionTab$Inclusion]]

length(AcceptedFinal)

RejectedFinal<-
  rbind(
    data.frame(id=names(reasonOK),reason=unlist(reasonOK)),
    data.frame(
      id=finalDecisionTab$abbrev[!is.na(finalDecisionTab$Inclusion)&!as.logical(finalDecisionTab$Inclusion)],
      reason=finalDecisionTab$ReasonExlusion[!is.na(finalDecisionTab$Inclusion)&!as.logical(finalDecisionTab$Inclusion)]
    ))
```

## rejection reason table

```{r}
kable(RejectedFinal,row.names = F)
```

## rejection reason numbers

```{r}
table(RejectedFinal$reason)
save(AcceptedFinal,file="../../screening/fullTextScreening/acceptedFinal.RData")
```

```{r}
rawExtract<-read.xlsx("../../extraction/20231022.xlsx",sheet = "extraction ",startRow = 2)
AcceptedFinal[!AcceptedFinal%in%rawExtract$id]
rawExtract$id[!rawExtract$id%in%AcceptedFinal]
length(unique(rawExtract$id))
length(AcceptedFinal)
```


## Missing decisions


```{r}
load("../../screening/fullTextScreening/FTS.RData")
docsTot<-unlist(FTS$description$documents)
(missin <- docsTot[!docsTot%in%AcceptedFinal & !docsTot%in%RejectedFinal$id])
  
```

Which assignments the missing decisions correspond to:
```{r}
if(length(missin)>0){
tabAssignMiss<-sapply(missin,function(x,l)
{
  sapply(l,function(y,x)x%in%y$documents,x=x)
},l=FTS$assignments
  )
colnames(tabAssignMiss)<-missin
apply(tabAssignMiss,2,which)
}
```