---
title: "Results from the extraction: graphs and numbers"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
always_allow_html: true
---

```{r}
require(openxlsx)&require(knitr)&require(kableExtra)
names(loadWorkbook("../../extraction/20231022.xlsx"))
rawExtract<-read.xlsx("../../extraction/20231022.xlsx",sheet = "extraction ",startRow = 2)
extract<-rawExtract
load("../../extraction/docExtract.RData")
```
# Missing extractions

```{r}
missin<-unlist(docExtract)[!unlist(docExtract)%in%extract$id]
missin<-missin[missin!="Saribaş2016"]
missin
```



# Dates

```{r}
rawExtract$datepubl
extract$datepubl<-as.integer(gsub("\\.0$","",gsub("^([A-Z][a-z]+ )([12][0-9]{3})","\\2",rawExtract$datepubl)))

(datesById<-tapply(extract$datepubl,extract$id,unique))
barplot(table(factor(datesById,levels=min(datesById):max(datesById))), las=2, main="Number of documents included in the analysis by year")
```


```{r}
A <- table(factor(datesById,levels=min(datesById):max(datesById)))
A[as.numeric(names(A))>=2012]
sum(A[as.numeric(names(A))>=2012])/sum(A)
```




# Countries

```{r}
library(stringr)
#rawExtract$Countries.STUDY
extract$Countries.STUDY[extract$id=="Arya2016"]<-"United States;China;New Zealand;Norway"
extract$Countries.STUDY<-gsub("Puerto Rico \\(United States\\)","United States",gsub("Estados Unidos","United States",gsub("BRASIL","Brazil",gsub("UK","United Kingdom",gsub("USA","United States",extract$Countries.STUDY)))))
sepCountry <- strsplit(extract$Countries.STUDY,"[,;]")
countryStudy<-data.frame(id=rep(rawExtract$id,sapply(sepCountry,length)),
           country=unlist(sepCountry))
countryStudy$country<-str_to_title(gsub(" +$","",gsub("^and ","",gsub("^ +","",countryStudy$country))))
(nbBycountry<-sort(tapply(countryStudy$id,countryStudy$country,function(x)length(unique(x))),decreasing = T))

```




## Making the map

```{r}
require(rnaturalearth)
require(sf)
worldMap_tot<-ne_countries(returnclass = "sf")
tinyCountries<-ne_download(type="admin_0_tiny_countries",returnclass = "sf")
namesCountries<-names(nbBycountry)
pbs<-namesCountries[!(namesCountries%in%worldMap_tot$name_long|namesCountries%in%worldMap_tot$name|namesCountries%in%tinyCountries$NAME)]
InTinyCountries <- namesCountries[!(namesCountries%in%worldMap_tot$name_long|namesCountries%in%worldMap_tot$name)&namesCountries %in% tinyCountries$NAME]

if(length(pbs>0)){warning("the following countries are not found and will be ignored:",pbs)}
nbBycountry<-nbBycountry[!namesCountries%in%pbs]
namesCountries<-names(nbBycountry)
orderCt<-match(namesCountries,worldMap_tot$name_long)
orderCt[is.na(orderCt)]<-match(namesCountries[is.na(orderCt)],worldMap_tot$name)
orderTinyCountries<-match(InTinyCountries,tinyCountries$NAME)
indexTinyCountries<-which(names(nbBycountry)%in%InTinyCountries)
#Colors
scaleNb<-rep(NA,length(nbBycountry))
scaleNb[nbBycountry==1]<-1
scaleNb[nbBycountry>1]<-2
scaleNb[nbBycountry>3]<-3
scaleNb[nbBycountry>5]<-4
scaleNb[nbBycountry>10]<-5
colorsScale<-c("#fafa6e","#f8cf55","#f6993c","#f35824","#ee0e0e")
par(mar=c(1,1,1,1))
plot(st_geometry(worldMap_tot),border="grey",lwd=0.5)
plot(st_geometry(worldMap_tot[orderCt,]),border="black",lwd=0.7,col=colorsScale[scaleNb],add=T)
plot(st_geometry(tinyCountries[orderTinyCountries,]),pch=22,bg = colorsScale[scaleNb[indexTinyCountries]],add=T,cex=.7)
legend("bottomleft",title="# Documents",fill=colorsScale,legend=c("1","2-3","4-5","5-10",paste0(">10 (USA: ",max(nbBycountry),")")))


countryStudy$FinalName<-NA
countryStudy$FinalName<-worldMap_tot[match(countryStudy$country,worldMap_tot$name),]$name
countryStudy$FinalName[countryStudy$country%in%InTinyCountries] <- tinyCountries$NAME[match(countryStudy$country[countryStudy$country%in%InTinyCountries],tinyCountries$NAME)]
countryStudy$FinalName[is.na(countryStudy$FinalName)]<-worldMap_tot[match(countryStudy$country[is.na(countryStudy$FinalName)],worldMap_tot$name_long),]$name

countryDoc <- tapply(countryStudy$FinalName,countryStudy$id,function(x)
  {
  if(length(unique(x))==1){return(x[1])}else{return("Multiple")}
})
```
# Years/Region of the world

```{r yearRegions,fig.height=7,fig.width=10}
REG<-factor(worldMap_tot$region_wb[worldMap_tot$region_wb!="Antarctica"])
plot(st_geometry(worldMap_tot[worldMap_tot$region_wb!="Antarctica",]),col=rainbow(nlevels(REG))[REG])
countryStudy$region<-NA
countryStudy$region<-worldMap_tot[match(countryStudy$country,worldMap_tot$name_long),"region_wb"]$region_wb
countryStudy$region[countryStudy$country%in%InTinyCountries] <- tinyCountries[match(countryStudy$country[countryStudy$country%in%InTinyCountries],tinyCountries$NAME),"REGION_WB"]$REGION_WB
countryStudy$region[is.na(countryStudy$region)]<-worldMap_tot[match(countryStudy$country[is.na(countryStudy$region)],worldMap_tot$name),"region_wb"]$region_wb
regionPapers<-factor(tapply(countryStudy$region,countryStudy$id,function(x){
  if(length(unique(x))==1){return(x[1])}else{return("Multiple")}
}),levels=c(levels(REG),"Multiple"))
yearPaper<-factor(datesById,levels=min(datesById):max(datesById))
TAB_year_region<-table(regionPapers,yearPaper[names(regionPapers)])
TAB_year_region<-TAB_year_region[as.logical(rowSums(TAB_year_region)),]
TAB_year_region<-TAB_year_region[order(rowSums(TAB_year_region),decreasing=T),]

A<-barplot(TAB_year_region,las=2,col=rainbow(nrow(TAB_year_region)),legend=T,args.legend = list(x="topleft"))
events <- c("United nations: Climate\nchange education framework","UNESCO: Climate Change\nEducation for Sustainable\nDevelopment program","Paris Agreement\nand SDG adoption")
dates <- c(1994,2010,2015)
events <-events[dates>min(as.numeric(colnames(TAB_year_region)))]
dates<-dates[dates>min(as.numeric(colnames(TAB_year_region)))]
datesOnGraph <-A[dates - as.numeric(min(as.numeric(colnames(TAB_year_region)), na.rm = T)) +1]
arrows(x0=datesOnGraph,y0=c(5,16),y1=rep(0,2),x1=datesOnGraph,length = .2,col="black", lwd=2)
text(datesOnGraph,c(6,16.5),events, cex=.7)
```

## Countries authors

```{r}
extract$Countries.AUTHORS<-gsub(" ?Puerto Rico \\(United States\\)","United States",gsub("Estados Unidos","United States",gsub("BRASIL","Brazil",gsub("England","United Kingdom",gsub("UK","United Kingdom",gsub("USA","United States",extract$Countries.AUTHORS))))))
sepCountryA<-strsplit(extract$Countries.AUTHORS,"[,;]")
countryStudyA<-data.frame(id=rep(rawExtract$id,sapply(sepCountryA,length)),
           country=unlist(sepCountryA))
countryStudyA$country<-str_to_title(gsub(" +$","",gsub("^and ","",gsub("^ +","",countryStudyA$country))))
countryStudyA$FinalName<-NA
countryStudyA$FinalName<-worldMap_tot[match(countryStudyA$country,worldMap_tot$name),]$name
countryStudyA$FinalName[countryStudyA$country%in%InTinyCountries] <- tinyCountries$NAME[match(countryStudyA$country[countryStudyA$country%in%InTinyCountries],tinyCountries$NAME)]
countryStudyA$FinalName[is.na(countryStudyA$FinalName)]<-worldMap_tot[match(countryStudyA$country[is.na(countryStudyA$FinalName)],worldMap_tot$name_long),]$name
A<-tapply(countryStudyA$FinalName,countryStudyA$id,function(x)x)
B<-tapply(countryStudy$FinalName,countryStudy$id,function(x)x)
names(A)==names(B)
res<-mapply(function(a,b)b[!b%in%a],A,B)
res<-res[sapply(res,function(x)length(x)>0)]
kable(extract[extract$id%in%names(res),c("Countries.AUTHORS","Countries.STUDY")])
```



## Income group

```{r incomegroup}
#countryDoc
incomeGrpDoc<-worldMap_tot[match(countryDoc,worldMap_tot$name),"income_grp"]$income_grp
incomeGrpDoc[is.na(incomeGrpDoc)&countryDoc%in%tinyCountries$NAME]<-tinyCountries[match(countryDoc[is.na(incomeGrpDoc)&countryDoc%in%tinyCountries$NAME],tinyCountries$NAME),"INCOME_GRP"]$INCOME_GRP
table(incomeGrpDoc,useNA="ifany")
par(mar=c(12,4,1,1))
barplot(table(incomeGrpDoc,useNA="ifany"),las=2)
countryDoc[is.na(incomeGrpDoc)]
```

Para referencia, number of countries with the different categories in the world

```{r countryOutcomes}
table(c(worldMap_tot$income_grp,tinyCountries$INCOME_GRP))
par(mar=c(12,4,1,1))
barplot(table(c(worldMap_tot$income_grp,tinyCountries$INCOME_GRP)),las=2)
```


```{r}
barplot(table(incomeGrpDoc,yearPaper,useNA="ifany"),col=rainbow(nlevels(factor(incomeGrpDoc))+1),legend=T,args.legend = list(x="topleft"))
```
```{r}
countryStudy$income_grp <- worldMap_tot[match(countryStudy$FinalName,worldMap_tot$name),]$income_grp
countryStudy$economy <- worldMap_tot[match(countryStudy$FinalName,worldMap_tot$name),]$economy
countryStudy$gdp_md <- worldMap_tot[match(countryStudy$FinalName,worldMap_tot$name),]$gdp_md
countryStudy$income_grp[is.na(countryStudy$income_grp)]<-tinyCountries[match(countryStudy$FinalName [is.na(countryStudy$income_grp)],tinyCountries$NAME),]$INCOME_GRP
countryStudy$economy[is.na(countryStudy$economy)]<-tinyCountries[match(countryStudy$FinalName[is.na(countryStudy$economy)],tinyCountries$NAME),]$ECONOMY
countryStudy$gdp_md[is.na(countryStudy$gdp_md)]<-tinyCountries[match(countryStudy$FinalName[is.na(countryStudy$gdp_md)],tinyCountries$NAME),]$GDP_MD

tapply(countryStudy$country,countryStudy$income_grp,unique)
tapply(countryStudy$country,countryStudy$economy,unique)

countryStudy$econFinal<-NA
countryStudy$econFinal[grepl("1",countryStudy$economy) | grepl("2",countryStudy$economy)] <- "Developed region"
countryStudy$econFinal[grepl("3",countryStudy$economy) | grepl("4",countryStudy$economy) | grepl("5",countryStudy$economy)] <- "Emerging region"
countryStudy$econFinal[grepl("^6",countryStudy$economy) | grepl("^7",countryStudy$economy)] <- "Developing region"
econDoc<-factor(sapply(tapply(countryStudy$econFinal, countryStudy$id, unique), function(x) if(length(x)>1){return(NA)}else{return(x)}),levels=c("Developed region","Emerging region","Developing region"), ordered=T)
barplot(table(econDoc,useNA="ifany"))


countryStudy$incomeFinal <- NA
countryStudy$incomeFinal [grepl("1",countryStudy$income_grp)|grepl("2",countryStudy$income_grp)] <- "High"
countryStudy$incomeFinal[grepl("3",countryStudy$income_grp)] <- "Middle to high"
countryStudy$incomeFinal [grepl("4",countryStudy$income_grp)|grepl("5",countryStudy$income_grp)] <- "Middle to low"

incomeDoc<-factor(sapply(tapply(countryStudy$incomeFinal, countryStudy$id, unique), function(x) if(length(x)>1){return(NA)}else{return(x)}), levels=c("High","Middle to high","Middle to low"), ordered=T)
barplot(table(incomeDoc,useNA="ifany"))
```


# Outcomes


```{r outcomes}
didItWork_col<-colnames(extract)[grep("it.work",colnames(extract))]
barplot(colSums(!is.na(extract[c("knowledge","awareness","intention","emotion","action","habit","Other")])))
withOutcome<-which(!is.na(extract[c("knowledge","awareness","intention","emotion","action","habit","Other")]),arr.ind=T)
outcomeEffect<-data.frame(id=extract$id[withOutcome[,1]],
           outcome=c("knowledge","awareness","intention","emotion","action","habit","Other")[withOutcome[,2]],
           effect=extract[didItWork_col][withOutcome]
           )
outcomeEffect$effect_simp<-NA
outcomeEffect$effect_simp[outcomeEffect$effect%in%c("yes","YES","Yes")]<-"Yes"
outcomeEffect$effect_simp[outcomeEffect$effect%in%c("no","No","NO")]<-"No"
outcomeEffect$effect_simp[is.na(outcomeEffect$effect_simp)]<-"Unclear"
tabOutEff<-table(factor(outcomeEffect$outcome,levels=c("knowledge","awareness","intention","emotion","action","habit","Other")),factor(outcomeEffect$effect_simp,levels=c("Yes","Unclear","No")),useNA="ifany")
kable(as.matrix(tabOutEff))
par(mar=c(6,4,1,1))
barplot(t(table(factor(outcomeEffect$outcome,levels=c("knowledge","awareness","intention","emotion","action","habit","Other")),factor(outcomeEffect$effect_simp,levels=c("Yes","Unclear","No")))),las=2, legend=T, args.legend = list(title="Efficient:"),names.arg = c("knowledge","awareness","intent","emotion","action","habit","Other"))

```

# Population


## Rural/urban

```{r rururb}
sort(table(extract$urban.vs.rural))
rururbClean<-factor(rep(NA,nrow(extract)),levels=c("Urban","Rural","Both","Not given"))
rururbClean[grep("^ ?urban ?$",extract$urban.vs.rural,ignore.case = T)]<-"Urban"
rururbClean[grep("^ ?rural ?$",extract$urban.vs.rural,ignore.case = T)]<-"Rural"
rururbClean[grep("^ ?both ?$",extract$urban.vs.rural,ignore.case = T)]<-"Both"
rururbClean[grepl("urban",extract$urban.vs.rural,ignore.case = T)&grepl("rural",extract$urban.vs.rural,ignore.case = T)]<-"Both"
table(extract$urban.vs.rural[is.na(rururbClean)])
table(rururbClean,useNA="ifany")
rururbClean[is.na(rururbClean)]<-"Not given"
barplot(table(rururbClean))
```

## categories


```{r}
extract$TARGETED.SAMPLE<-gsub(" $","",extract$TARGETED.SAMPLE)
sort(table(extract$TARGETED.SAMPLE,useNA="ifany"),decreasing=T)
#For student ages
extract$student<-extract$TARGETED.SAMPLE%in%c("Students","students")

# For population categories
extract$students<-grepl("student",extract$TARGETED.SAMPLE,ignore.case = T)
extract$teachers<-grepl("teacher",extract$TARGETED.SAMPLE,ignore.case = T)&extract$TARGETED.SAMPLE!="pre-service teachers"
extract$PS_teachers<-extract$TARGETED.SAMPLE=="pre-service teachers"
extract$parents<-grepl("parent",extract$TARGETED.SAMPLE,ignore.case = T)
resPopul<-by(extract[c("students","teachers","PS_teachers","parents")],extract$id,function(tab)
{
  popul<-apply(tab,2,any)
  if(length(popul[popul])>1){return("mixed")}else{return(names(popul)[popul])}
},simplify = T
  )
populClean<-Reduce(c,resPopul)
names(populClean)<-names(resPopul)
populClean[populClean=="students"]<-"Students"
populClean[populClean=="teachers"]<-"Teachers"
populClean[populClean=="PS_teachers"]<-"Pre-service teachers"
populClean[populClean=="parents"]<-"Parents"
populClean[populClean=="mixed"]<-"Mixed"
populClean<-factor(populClean,levels=names(sort(table(populClean),decreasing = T)))
par(mar=c(10,4,1,1))
barplot(table(populClean,useNA = "ifany"),las=2)
```

Clean, by row:

```{r}
pop <- factor(rep(NA,nrow(extract)),c("Students","Teachers","Pre-service teachers","Parents"))
pop[tolower(extract$TARGETED.SAMPLE)=="students"]<-"Students"
pop[tolower(extract$TARGETED.SAMPLE)%in%c("teachers","entourage (teachers)")] <- "Teachers"
pop[tolower(extract$TARGETED.SAMPLE)%in%c("pre-service teachers")] <- "Pre-service teachers"
pop[tolower(extract$TARGETED.SAMPLE)%in%c("parents","entourage (parents)")] <- "Parents"
```

**Calculated for manuscript**:

```{r}
table(populClean,useNA = "ifany")
table(populClean,useNA = "ifany")/sum(table(populClean,useNA = "ifany"))
sum(table(populClean,useNA = "ifany")[c("Teachers","Pre-service teachers")])/sum(table(populClean,useNA = "ifany"))
```




## Age 

```{r}
extract$idRow<-rownames(extract)
extract$age_min[extract$student]
extract$age_max[extract$student]
extract$mean.age[extract$student]
extract$age_min_stud<-NA
extract$age_max_stud<-NA
extract$age_aver_stud<-NA
extract$age_stud_no_info<-NA
extract$age_min_stud[extract$student]<-as.numeric(gsub(" \\[Extracted from grade\\]","",extract$age_min[extract$student]))
extract$age_max_stud[extract$student]<-as.numeric(gsub(" \\[Extracted from grade\\]","",extract$age_max[extract$student]))
extract$age_aver_stud[extract$student]<-as.numeric(gsub("\\[Extracted from grade\\]","",extract$mean.age[extract$student]))
extract[extract$student,"age_stud_no_info"]<-apply(extract[extract$student,c("age_min_stud","age_max_stud","age_aver_stud")],1,function(x)all(is.na(x)))
extract[extract$student,"age_stud_type_info"]<-apply(extract[extract$student,c("age_min_stud","age_max_stud","age_aver_stud")],1,function(x){
    if(!is.na(x[1]) & !is.na(x[2]) & !is.na(x[3])){return("all")}
    if(!is.na(x[1]) & !is.na(x[2]) & is.na(x[3])){return("minmax")}
    if(is.na(x[1]) & is.na(x[2]) & !is.na(x[3])){return("mean")}
    if(sum(!is.na(x[1]) & !is.na(x[2]))==1 ){return("missingminmax")}else{return(NA)}
    
  })

#extract[extract$student,c("age_min","age_max","mean.age","age_min_stud","age_max_stud","age_aver_stud","age_stud_no_info","age_stud_type_info")]
table(extract$age_stud_type_info[extract$student],useNA = "always")
age_order<- rep(NA,sum(!is.na(extract$age_stud_type_info)))
age_order[extract$age_stud_type_info[!is.na(extract$age_stud_type_info)]%in%c("all","mean")]<- extract[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info%in%c("all","mean"),"age_aver_stud"]
age_order[extract$age_stud_type_info[!is.na(extract$age_stud_type_info)]%in%c("minmax")]<-rowMeans( extract[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info%in%c("minmax"),c("age_min_stud","age_max_stud")])
order(age_order)
tabForPlot<-extract[!is.na(extract$age_stud_type_info),c("idRow","age_min_stud","age_max_stud","age_aver_stud","age_stud_no_info","age_stud_type_info")]
tabForPlot$pop<-pop[!is.na(extract$age_stud_type_info)]
tabForPlot<-tabForPlot[order(age_order),]
plot(x=age_order[order(age_order)],y=1:nrow(tabForPlot),type="n",xlim=range(tabForPlot[,c("age_min_stud","age_max_stud")],na.rm=T), xlab="Age",ylab="",yaxt="n")
segments(tabForPlot$age_min_stud[tabForPlot$age_stud_type_info%in%c("minmax","all")],(1:nrow(tabForPlot))[tabForPlot$age_stud_type_info%in%c("minmax","all")], tabForPlot$age_max_stud[tabForPlot$age_stud_type_info%in%c("minmax","all")])
points(tabForPlot$age_aver_stud[tabForPlot$age_stud_type_info%in%c("mean","all")],(1:nrow(tabForPlot))[tabForPlot$age_stud_type_info%in%c("mean","all")],pch=3,cex=.5)
```

### Adding ages from grades

```{r fig.height=6,fig.width=7}
extract[is.na(extract[,"age_stud_type_info"])&!is.na(as.numeric(extract$Age_min.from.grade.))&!is.na(as.numeric(extract$Age_max.from.grade)),"age_stud_type_info"]<-"minmaxFromGrade"
tabForPlot<-rbind(
  tabForPlot,
  data.frame(idRow=extract$idRow[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info=="minmaxFromGrade"],
             age_min_stud=as.numeric(extract$Age_min.from.grade.[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info=="minmaxFromGrade"]),
             age_max_stud=as.numeric(extract$Age_max.from.grade[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info=="minmaxFromGrade"]),
             age_aver_stud=NA,
             age_stud_no_info=T,
             age_stud_type_info="minmaxFromGrade",
             pop=pop[!is.na(extract$age_stud_type_info)&extract$age_stud_type_info=="minmaxFromGrade"])
)
tabForPlot<-tabForPlot[!is.na(tabForPlot$pop)&tabForPlot$pop=="Students",]
tabForPlot$medianVal<-NA
tabForPlot$medianVal[tabForPlot$age_stud_type_info%in%c("minmaxFromGrade","minmax")]<-rowMeans(tabForPlot[tabForPlot$age_stud_type_info%in%c("minmaxFromGrade","minmax"),c("age_min_stud","age_max_stud")])
tabForPlot$medianVal[tabForPlot$age_stud_type_info%in%c("all","mean")]<-tabForPlot$age_aver_stud[tabForPlot$age_stud_type_info%in%c("all","mean")]
tabForPlot<-tabForPlot[order(tabForPlot$medianVal),]
plot(x=tabForPlot$medianVal,y=1:nrow(tabForPlot),type="n",xlim=range(tabForPlot[,c("age_min_stud","age_max_stud")],na.rm=T), xlab="Age",ylab="",yaxt="n")
segments(tabForPlot$age_min_stud[tabForPlot$age_stud_type_info%in%c("minmax","all")],(1:nrow(tabForPlot))[tabForPlot$age_stud_type_info%in%c("minmax","all")], tabForPlot$age_max_stud[tabForPlot$age_stud_type_info%in%c("minmax","all")])
segments(tabForPlot$age_min_stud[tabForPlot$age_stud_type_info%in%c("minmaxFromGrade")],(1:nrow(tabForPlot))[tabForPlot$age_stud_type_info%in%c("minmaxFromGrade")], tabForPlot$age_max_stud[tabForPlot$age_stud_type_info%in%c("minmaxFromGrade")],lty=3)
points(tabForPlot$age_aver_stud[tabForPlot$age_stud_type_info%in%c("mean","all")],(1:nrow(tabForPlot))[tabForPlot$age_stud_type_info%in%c("mean","all")],pch=3,cex=.5)
legend("topleft",lwd=c(1,.5,NA),lty=c(1,3,NA),pch=c(NA,NA,3),legend=c("Range given","Range from grades","Average given"))
```



## Population final categories

```{r}
extract[c("age_stud_type_info","age_min_stud","age_max_stud","age_aver_stud","TARGETED.SAMPLE")]

table(extract$age_stud_type_info,tolower(extract$TARGETED.SAMPLE))

table(extract$age_stud_type_info,pop,useNA="ifany")
extract$age_min_stud[is.na(extract$age_min_stud)]<-as.integer(extract$Age_min.from.grade.[is.na(extract$age_min_stud)])
extract$age_max_stud[is.na(extract$age_max_stud)]<-as.integer(extract$Age_max.from.grade[is.na(extract$age_max_stud)])
ageConcerned<-t(sapply(
  mapply(function(a,b)if(is.na(a)){return(NA)}else{return(a:b)},extract$age_min_stud,extract$age_max_stud),
  function(x,a,b)a:b%in%x,a=min(extract$age_min_stud,na.rm = T),b=max(extract$age_max_stud, na.rm = T)
                                ))
colnames(ageConcerned)<- min(extract$age_min_stud,na.rm = T): max(extract$age_max_stud, na.rm = T)
stopifnot(nrow(ageConcerned[is.na(extract$age_min_stud)&!is.na(extract$age_aver_stud),])==0)
agesThreshold<-c(4,11,15,19)
categoriesCol <- cut(
  min(extract$age_min_stud,na.rm = T): max(extract$age_max_stud, na.rm = T),
  breaks=agesThreshold+c(rep(0,length(agesThreshold)-1),0.0000001),
  right = T,include.lowest = T,
  labels=paste(agesThreshold[1:(length(agesThreshold)-1)]+c(0,rep(1,length(agesThreshold)-2)),agesThreshold[2:length(agesThreshold)],sep="-")
                  )
catAgeConcerned<-sapply(tapply(colnames(ageConcerned),categoriesCol,function(x)x),
       function(x,mat)apply(mat[,x],1,any),mat=ageConcerned)
catAgeConcernedWeight<-sapply(tapply(colnames(ageConcerned),categoriesCol,function(x)x),
       function(x,mat)apply(mat[,x],1,sum),mat=ageConcerned)
```


```{r}
barplot(colSums(catAgeConcerned))
```


Number of age categories by study:

```{r}
barplot(table(rowSums(catAgeConcerned)))
```


```{r}
rangeByStudyText<-apply(catAgeConcerned,1,function(x,cat)paste(paste(cat[x],sep=""),collapse=", "),cat=colnames(catAgeConcerned))
popTot<-mapply(function(a,b)
  {
    if(is.na(a)){return(NA)}
    if(a=="Students"){return(paste0("Students (",ifelse(b=="","no age information",b),")"))}else{return(as.character(a))}
  },pop,rangeByStudyText)
par(mar=c(12,4,1,1))
unique(popTot)
popTot<-factor(popTot,
               levels=c("Students (4-11)",
                        "Students (4-11, 12-15)",
                        "Students (4-11, 12-15, 16-19)",
                        "Students (12-15)",
                        "Students (12-15, 16-19)",
                        "Students (16-19)",
                        "Students (no age information)",
                        "Teachers",
                        "Pre-service teachers",
                        "Parents"
                        ),
               labels=c("Students (4-11)",
                        "Students (4-15)",
                        "Students (4-19)",
                        "Students (12-15)",
                        "Students (12-19)",
                        "Students (16-19)",
                        "Students (no age information)",
                        "Teachers",
                        "Pre-service teachers",
                        "Parents"
                        ))
barplot(table(popTot,useNA = "ifany"),las=2)
```


```{r creationTabAge}
catAgeConcerned_df<- data.frame(
  id=extract$id,
  idRow=rownames(extract),
  catAgeConcerned
)
```



```{r}
catAgeConcerned<-cbind(catAgeConcerned,`No age information`=(apply(catAgeConcerned,1,sum)==0))
w_age<-which(catAgeConcerned,arr.ind=T)
AgeByRow<-data.frame(
  idRow=w_age[,"row"],
  ageCat=colnames(catAgeConcerned)[w_age[,"col"]]
)
```



# Controversy

```{r}
table(extract$Controversy,useNA="always")
extract$controv_clean<-NA
extract$controv_clean[grep("no",extract$Controversy,ignore.case=T)]<-"No"
extract$controv_clean[grep("yes",extract$Controversy,ignore.case=T)]<-"Yes"
#extract[c("controv_clean","Controversy")]
table(extract$controv_clean,useNA="ifany")
controvByDoc<-tapply(extract$controv_clean,extract$id,function(x)
  {
    if(any(na.omit(x)=="Yes")){return("Yes")}else if(any(na.omit(x)=="No")){return("No")}else{return(NA)}
  })
(A<-table(countryDoc[names(controvByDoc)],factor(controvByDoc,levels=c("No","Yes")),useNA="ifany"))
(PercentageControversy<-A[,2]/rowSums(A))
barplot(PercentageControversy,las=2)
sum(controvByDoc=="Yes"&countryDoc[names(controvByDoc)]=="United States of America",na.rm = T)/sum(controvByDoc=="Yes",na.rm=T)
sum(countryDoc[names(controvByDoc)]=="United States of America",na.rm=T)/length(countryDoc)
sum(controvByDoc=="Yes"&countryDoc[names(controvByDoc)]=="United States of America",na.rm = T)/sum(countryDoc[names(controvByDoc)]=="United States of America",na.rm=T)
par(mar=c(11,4,1,1))
barplot(t(A[order(A[,2],A[,1],decreasing=T),1:2]),beside=T,col=c("blue","red"),las=2,legend=T,args.legend = list(title="Controversy"))
```

**Calculations for text**

```{r}
A["United States of America","Yes"]/sum(A[,"Yes"])
sum(A["United States of America",])/sum(A)
A["United States of America",]/sum(A["United States of America",])
A[as.logical(A[,"Yes"]),]
docMultipleCountries <- names(countryDoc)[countryDoc=="Multiple"]
countriesMultipleCountries<-countryStudy[countryStudy$id %in% docMultipleCountries,]
kbl(data.frame(
  controversy=controvByDoc[docMultipleCountries],
  countries=tapply(countriesMultipleCountries$country,countriesMultipleCountries$id,paste,collapse=", ")[docMultipleCountries],
  row.names = docMultipleCountries
))
```



# Mitigation/Adaptation

```{r}
table(extract$`Final.mitigation/adaptation`,useNA = 'always')/sum(table(extract$`Final.mitigation/adaptation`,useNA = 'always'))
barplot(table(factor(extract$`Final.mitigation/adaptation`,levels=c("Mitigation","Adaptation","Both","Neither"))))
```
# Disciplines


```{r}
par(mar=c(8,4,1,1))
sort(table(extract$Disciplin_2))
disciplineClean<- extract$Disciplin_2
disciplineClean[grepl("^Social",extract$Disciplin_2)]<-"Social Sciences"
disciplineClean[grepl("STEAM",extract$Disciplin_2)]<-"Mixed"
disciplineClean[grepl("NA",extract$Disciplin_2)|is.na(extract$Disciplin_2)]<-"ND"
barplot(sort(table(disciplineClean),decreasing=T), las=2)
```


# Educational framework

We've got a problem, most of the extracted papers just do not have the information:

```{r}
edFrameNb<-table(extract$`Normative.Climate.Change.EDUCATIONAL.framework.(global/local)`,useNA="ifany")
edFrameNb<-edFrameNb[order(edFrameNb,decreasing=T)]

tabEdFrame<-data.frame(
    EducationalFramework=names(edFrameNb),
    nb=as.numeric(edFrameNb),
    ids=sapply(names(edFrameNb),function(x,tab)paste(na.omit(tab$id[tab$`Normative.Climate.Change.EDUCATIONAL.framework.(global/local)`==x]),collapse=", "), tab=extract)
  ,row.names = NULL)
tabEdFrame[is.na(tabEdFrame$EducationalFramework),3]<-paste(extract$id[is.na(extract$`Normative.Climate.Change.EDUCATIONAL.framework.(global/local)`)],collapse=", ")
kable(tabEdFrame)

```


# Monroe categories

How many include "5:target climate science misconceptions":

```{r}
sum(grepl("5",extract$`Monroe.categories.(ONLY.1,2,3,4,5,6,7)`))
```

Which:

```{r}
extract$id[grepl("5",extract$`Monroe.categories.(ONLY.1,2,3,4,5,6,7)`)]
```

# Theoretical framework


```{r fig.height=7,fig.width=6}
#sort(table(extract$`Theoretical.framework.(big.categories)`))
clean<-function(x)
{
  if(grepl("^ *$",x)){x<-NA}
  x<-gsub("^ +","",x)
  x<-gsub(" +$","",x)
  x<-gsub("^([a-z])","\\U\\1",x,perl=T)
  return(x)
}
extract$`Theoretical.framework.(big.categories)`<-gsub("^ ","",gsub(" $","",gsub("^([a-zA-Z])(.*)","\\U\\1\\L\\2",extract$`Theoretical.framework.(big.categories)`,perl=T),perl=T),perl=T)
listTheoBack<-lapply(strsplit(extract$`Theoretical.framework.(big.categories)`,"[,;]"),sapply,clean)
tabTheoBack<-data.frame(
  idRow=rep(rownames(extract),sapply(listTheoBack,length)),
  id=rep(extract$id,sapply(listTheoBack,length)),
           theoBack=unlist(listTheoBack)
           )
#Temporary plot
forTempPlot<-table(tabTheoBack$theoBack)
forTempPlot<-forTempPlot[order(forTempPlot,decreasing=T)]
#other<-(forTempPlot[6:nrow(forTempPlot)])
#forTempPlot<-forTempPlot[1:5]
#forTempPlot<-c(forTempPlot,other)
par(mar=c(15,4,1,1))
bp<-barplot(forTempPlot,las=2)
#legend("topright",density=18,"consistent with")
#text(bp[round(nrow(forTempPlot)/4)+1],max(forTempPlot)-5,paste("To evaluate:",sum(is.na(tabTheoBack$theoBack))))

kable(sort(table(tabTheoBack$theoBack),decreasing=T))
```

## Comparison with population
```{r fig.height=7,fig.width=6}
par(mar=c(15,4,1,1))
barplot(as.matrix(table(popTot,extract$`Theoretical.framework.(big.categories)`)),col=rainbow(nlevels(popTot)), las=2, legend=T)
kable(as.matrix(table(popTot,extract$`Theoretical.framework.(big.categories)`,useNA="ifany")))
```

## Comparison with pedagogical tools

```{r fig.height=7,fig.width=6}
par(mar=c(15,4,1,1))
extract$Categories.type.of.intervention<-factor(extract$Categories.type.of.intervention)
barplot(table(extract$Categories.type.of.intervention,extract$`Theoretical.framework.(big.categories)`),col=rainbow(nlevels(extract$Categories.type.of.intervention)),las=2,legend=T)
```


# Methods & design

## Quanti/Quali
```{r}
sort(table(extract$study.type),decreasing = T)
extract$QuantQualClean<-NA
extract$QuantQualClean[grep("quantitative",ignore.case = T, extract$study.type)]<-"Quantitative"
extract$QuantQualClean[grep("qualitative",ignore.case = T, extract$study.type)]<-"Qualitative"
extract$QuantQualClean[grepl("mixed",ignore.case = T, extract$study.type) | grepl("both",ignore.case = T, extract$study.type)]<-"Both/Mixed"
sort(table(extract$QuantQualClean,useNA = "ifany"),decreasing = T)
barplot(sort(table(extract$QuantQualClean),decreasing = T))
```

## Pre-post

```{r,fig.height=5}
table(extract$`Pre/Post`)
extract$`Pre/Post`<-(grepl("true",extract$`Pre/Post`, ignore.case = T) | grepl("verdadero",extract$`Pre/Post`, ignore.case = T) | grepl("vrai",extract$`Pre/Post`, ignore.case = T) | grepl("yes",extract$`Pre/Post`, ignore.case = T))
(tabMetodosAnalyses <- table(extract$`Pre/Post`,extract$QuantQualClean,useNA="ifany"))
colSums(tabMetodosAnalyses)/sum(tabMetodosAnalyses)
barplot(table(extract$`Pre/Post`,extract$QuantQualClean,useNA="ifany"), legend=T,args.legend = list(x="topleft",title="Pre/post"))
```




```{r}
A<-sort(table(extract$design),decreasing=T)
names(A)[nchar(names(A))>40]<-paste(substr(names(A)[nchar(names(A))>40],1,40),"...")
A
extract$prepostClean<-NA
extract$`Pre/Post`[!extract$`Pre/Post`%in%c("TRUE","TRUE ","VRAI","verdadero","VERDADERO","Verdadero","Yes","yes","YES","FALSE","FALSO","FAUX","Falso","No","no")]
extract$prepostClean[extract$`Pre/Post`%in%c("TRUE","TRUE ","VRAI","verdadero","VERDADERO","Verdadero","Yes","yes","YES")]<-T
extract$prepostClean[extract$`Pre/Post`%in%c("FALSE","FALSO","FAUX","Falso","No","no")]<-F

#table(extract$design[extract$prepostClean])
#table(extract$design[!extract$prepostClean])

#extract$design[grepl("pre ?-? ?post",extract$design,ignore.case = T)]
desPrePost<-grepl("pre ?-? ?post",extract$design,ignore.case = T)
pControl<-grepl("pre ?-? ?post",extract$design,ignore.case = T) & grepl("\\+",extract$design) & grepl("control",extract$design,ignore.case = T)
pFactor <-grepl("pre ?-? ?post",extract$design,ignore.case = T) & grepl("\\+",extract$design) & grepl("factor",extract$design,ignore.case = T)
pDuring <-grepl("pre ?-? ?post",extract$design,ignore.case = T) & grepl("\\+",extract$design) & grepl("during",extract$design,ignore.case = T)
designClean<-character(nrow(extract))
designClean[desPrePost &! pControl &! pFactor & !pDuring]<- "Pre-post"
designClean[desPrePost & pControl & !pFactor & !pDuring]<- "Pre-post + Control"
designClean[desPrePost & !pControl & pFactor & !pDuring]<- "Pre-post + Factor"
designClean[desPrePost & !pControl & !pFactor & pDuring]<- "Pre-post + During"
designClean[desPrePost & pControl & pFactor & !pDuring]<- "Pre-post + Factor + Control"
extract$design[desPrePost&designClean==""]
table(extract$design[!desPrePost])[table(extract$design[!desPrePost])>1]
designClean[designClean==""&grepl("case study",extract$design,ignore.case = T)]<-"Case study"
designClean[designClean==""&grepl("discourse analysis",extract$design,ignore.case = T)]<-"Discourse analysis"
designClean[designClean==""]<-"Other"
designClean<-factor(designClean,levels=c("Pre-post", "Pre-post + Control", "Pre-post + Factor", "Pre-post + Factor + Control", "Pre-post + During", "Case study",  "Discourse analysis", "Other"))
barplot(table(designClean),las=2)
```


```{r, fig.height=5,fig.width=7}
par(mfrow=c(1,2))
par(mar=c(11,4,1,1))
barplot(table(designClean),las=2)
barplot(sort(table(extract$QuantQualClean),decreasing = T),las=2)
```

# Characteristics of interventions
## Pedagogical tools


### From manuscript 1 text
```{r}
par(mar=c(9,4,1,1))
barplot(c(
  `Lesson based`=40,
  `Combined strategy`=38,
  `Project based`=19,
  `Curriculum based`=15,
  `Technology/Virtual`=9,
  `Cultural based`=8,
  `Game based`=4
), las = 2
)
```

### From table

```{r, fig.height=5, fig.width=5}
par(mar=c(14,4,1,1))
barplot(sort(table(extract$Categories.type.of.intervention),decreasing=T),las=2)
extract$Categories.type.of.intervention <- extract$Categories.type.of.intervention <-factor(extract$Categories.type.of.intervention, levels = names(sort(table(extract$Categories.type.of.intervention), decreasing=T)))
```

### Over time
```{r,fig.width=15, fig.height=7}
opar <- par(lwd = 0.4)
barplot(table(extract$Categories.type.of.intervention,factor(extract$datepubl,levels=min(extract$datepubl):max(extract$datepubl))),beside=T,col=rainbow(nlevels(extract$Categories.type.of.intervention)), legend=T, args.legend=list(x="topleft"), lwd=.1, cex.names=.8)
```


## Curricular/extracurricular

```{r}
table(extract$`Curricular/Extracurricular`)
curExtraCur<-rep(NA,nrow(extract))
curExtraCur[extract$`Curricular/Extracurricular`%in%c("Curricular","Extracurricular")]<-extract$`Curricular/Extracurricular`[extract$`Curricular/Extracurricular`%in%c("Curricular","Extracurricular")]
curExtraCur[extract$`Curricular/Extracurricular`%in%c("CurricularandExtracurricular")] <- "Curricular/Extracurricular" 
curExtraCur[extract$`Curricular/Extracurricular`%in%c("ProfessionalDevelopment")] <- "Professional development" 
extract[c("Curricular/Extracurricular","id")][is.na(curExtraCur),][c(3,6,7),]
curExtraCur[extract$id=="Leitao2022"]<- c("Curricular/Extracurricular")
curExtraCur[extract$id=="Hu2016"]<-"Extracurricular"
curExtraCur[extract$id=="Korsager2015"]<-"Curricular"
par(mar=c(12,4,1,1))
barplot(table(curExtraCur,useNA="ifany"),las=2)
```


## Indoor/outdoor

```{r}
extract$`Outdoor/Indoor/Both`<-gsub("^([a-zA-Z])(.*)$","\\U\\1\\L\\2",extract$`Outdoor/Indoor/Both`,perl=T)
table(extract$`Outdoor/Indoor/Both`,useNA="ifany")
```



# Time variables

```{r}
extract$Total.duration.of.the.intervention
extract$Period.length
extract$Number.of.sessions
```

```{r}
hist(as.integer(gsub("^~","",extract$Number.of.sessions)),main="",xlab="Number of sessions", ylab="Number of studies",nclass=50)
legend("topright",legend=paste(c("n="),c(sum(!is.na(extract$Number.of.sessions)))),bty = "n")
```

```{r}
extract$Total.duration.of.the.intervention
extract$Total.duration.of.the.intervention[!is.na(extract$Total.duration.of.the.intervention)&!grepl("^(~)?(([0-9]+)([hH]))?(([0-9]+)(min))?",extract$Total.duration.of.the.intervention)]
totalDur<-data.frame(
  id=extract$id,
  raw=extract$Total.duration.of.the.intervention,
  ND=is.na(extract$Total.duration.of.the.intervention),
  approx=gsub("^(~)?(([0-9]+)([hH]))?(([0-9]+)(min))?","\\1",extract$Total.duration.of.the.intervention,perl=T)=="~",
  h=as.integer(gsub("^(~)?(([0-9]+)([hH]))?(([0-9]+)(min))?","\\3",extract$Total.duration.of.the.intervention,perl=T)),
  min=as.integer(gsub("^(~)?(([0-9]+)([hH]))?(([0-9]+)(min))?","\\6",extract$Total.duration.of.the.intervention,perl=T))
)
totalDur$totalMin=ifelse(totalDur$ND,NA,(60*ifelse(is.na(totalDur$h),0,totalDur$h))+ifelse(is.na(totalDur$min),0,totalDur$min))
kbl(totalDur[!totalDur$ND,])
hist(totalDur$totalMin,nclass=50,main="",xlab="Total intervention time",ylab="Number of studies",xaxt="n")
axis(1,at=c(0,60*c(20,50,100,150)),labels=c("0","20h","50h","100h","150h"),las=1)
legend("topright",legend=paste(c("n=","approximate values:"),c(sum(!totalDur$ND),sum(totalDur$approx,na.rm = T))),bty = "n")
```

```{r}
extract$Period.length
all(is.na(extract$Period.length[!grepl("^(~)?(([0-9]+)([Y]))?(([0-9]+)(M))?(([0-9]+)(D))?(([0-9]+)(H))?$",extract$Period.length)]))
perLen<-data.frame(
  id=extract$id,
  raw=extract$Period.length,
  ND=is.na(extract$Period.length),
  approx=gsub("^(~)?([0-9]+[Y])?([0-9]+M)?([0-9]+D)?([0-9]+H)?$","\\1",extract$Period.length,perl=T)=="~",
  Y=as.integer(gsub("^(~)?(([0-9]+)([Y]))?([0-9]+M)?([0-9]+D)?([0-9]+H)?$","\\3",extract$Period.length,perl=T)),
  M=as.integer(gsub("^(~)?([0-9]+[Y])?(([0-9]+)M)?([0-9]+D)?([0-9]+H)?$","\\4",extract$Period.length,perl=T)),
  D=as.integer(gsub("^(~)?([0-9]+[Y])?([0-9]+M)?(([0-9]+)D)?([0-9]+H)?$","\\5",extract$Period.length,perl=T)),
  H=as.integer(gsub("^(~)?([0-9]+[Y])?([0-9]+M)?([0-9]+D)?(([0-9]+)H)?$","\\6",extract$Period.length,perl=T))
)
perLen$totalHours=ifelse(perLen$ND,NA,
                         (364*24*ifelse(is.na(perLen$Y),0,perLen$Y))
                         +(30.5*24*ifelse(is.na(perLen$M),0,perLen$M))
                         +(24*ifelse(is.na(perLen$D),0,perLen$D))
                         +(ifelse(is.na(perLen$H),0,perLen$H))
                         )
kbl(perLen[!perLen$ND,])
hist(perLen$totalHours,nclass=200,main="",xlab="Total intervention period length",ylab="Number of studies",xaxt="n")
axis(1,at=c(1,24,24*7,24*30.5,24*364,24*364*2,24*364*3),labels=c(NA,NA,"week","month","year","2 years","3 years"),las=1)
legend("topright",legend=paste(c("n=","approximate values:"),c(sum(!perLen$ND),sum(perLen$approx,na.rm = T))),bty = "n")
```

## intervention time categories

```{r}
recapTempInterv <- data.frame(
id=extract$id,
nbSessions = as.integer(gsub("^~","",extract$Number.of.sessions)),
totalDur_min = totalDur$totalMin,
perLen_h = perLen$totalHours
)
kable(recapTempInterv)
recapTempInterv$category<-NA
recapTempInterv$category[recapTempInterv$nbSessions==1&recapTempInterv$totalDur_min<=180]<-"1 session of 3h or less"
recapTempInterv$category[recapTempInterv$nbSessions>1&recapTempInterv$totalDur_min<=180]<-"multiples sessions total contact time of 3h or less"
recapTempInterv$category[is.na(recapTempInterv$category) & (recapTempInterv$perLen_h > 3 & recapTempInterv$perLen_h <= 24*7 )] <- "Total period 1 week or less"
recapTempInterv$category[is.na(recapTempInterv$category) & ( recapTempInterv$perLen_h > 7*24 & recapTempInterv$perLen_h <= 30*24)] <- "Total period span more than 1 week"
recapTempInterv$category[is.na(recapTempInterv$category) & ( recapTempInterv$perLen_h > 30*24 )] <- "Total period span more than 1 month"
recapTempInterv$category<-factor(recapTempInterv$category,levels=c(
  "1 session of 3h or less",
  "multiples sessions total contact time of 3h or less",
  "Total period 1 week or less",
  "Total period span more than 1 week",
  "Total period span more than 1 month"
), labels = c("very short unique", "very short multiple", "week period", "month period", "large period"))

table(recapTempInterv$category,useNA = "ifany")

kable(recapTempInterv[!is.na(recapTempInterv$category) & recapTempInterv$category=="very short unique",])
kable(recapTempInterv[!is.na(recapTempInterv$category) & recapTempInterv$category=="very short multiple",])
kable(recapTempInterv[!is.na(recapTempInterv$category) & recapTempInterv$category=="week period",])
kable(recapTempInterv[!is.na(recapTempInterv$category) & recapTempInterv$category=="month period",])
kable(recapTempInterv[!is.na(recapTempInterv$category) & recapTempInterv$category=="large period",])
kable(recapTempInterv[is.na(recapTempInterv$category),])

write.xlsx(recapTempInterv,file="../../extraction/timeIntervWork.xlsx")

```



```{r}
extract$Intervention.time.category<-factor(extract$Intervention.time.category,levels=c("very short unique", "very short multiple", "week period", "month period", "large period"), ordered=T)
table(extract$Intervention.time.category)
```

## Horizon of change

```{r}
extract$Horizon.of.change<-gsub("^([a-z])" , replacement= "\\U\\1" , extract$Horizon.of.change, perl=T)
extract$Horizon.of.change<-gsub("-" , replacement= " " , extract$Horizon.of.change, perl=T)
extract$Horizon.of.change<-factor(extract$Horizon.of.change, levels=c("Very short term", "Short term", "Middle term", "Long term"))
table(extract$Horizon.of.change)
```

## Comparison

### Between time aspects

```{r, fig.width=12}
kable(table(extract$Horizon.of.change,extract$Intervention.time.category,useNA = "ifany"))
barplot(table(extract$Horizon.of.change,extract$Intervention.time.category,useNA = "ifany"),beside = T,legend=T, args.legend = list(title="Horizon of change"))
```


### With outcomes

```{r fig.height=15, fig.width=10}
tf_outcomes <- !is.na(extract[c("knowledge","awareness","intention","emotion","action","habit","Other")])
didItWork_outcomes <- matrix(factor("Unclear",levels=c("Yes","No","Unclear")),nrow=nrow(tf_outcomes),ncol=ncol(tf_outcomes))
dimnames(didItWork_outcomes)<-dimnames(tf_outcomes)
didItWork_outcomes[which(as.matrix(extract[,didItWork_col])%in%c("Yes","yes","YES"),arr.ind=T)]<-"Yes"
didItWork_outcomes[which(as.matrix(extract[didItWork_col])%in%c("no","No","NO"),arr.ind=T)]<-"No"
didItWork_outcomes[which(!tf_outcomes,arr.ind=T)]<-NA



par(mar=c(8,4,3,1),mfrow=c(3,2))
barplot(table(didItWork_outcomes[tf_outcomes[,"knowledge"],"knowledge"],extract$Intervention.time.category[tf_outcomes[,"knowledge"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Knowledge")
barplot(table(didItWork_outcomes[tf_outcomes[,"awareness"],"awareness"],extract$Intervention.time.category[tf_outcomes[,"awareness"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Awareness")
barplot(table(didItWork_outcomes[tf_outcomes[,"intention"],"intention"],extract$Intervention.time.category[tf_outcomes[,"intention"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Intent")
barplot(table(didItWork_outcomes[tf_outcomes[,"emotion"],"emotion"],extract$Intervention.time.category[tf_outcomes[,"emotion"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Emotion")
barplot(table(didItWork_outcomes[tf_outcomes[,"action"],"action"],extract$Intervention.time.category[tf_outcomes[,"action"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Action")
barplot(table(didItWork_outcomes[tf_outcomes[,"habit"],"habit"],extract$Intervention.time.category[tf_outcomes[,"habit"]]), las=2, legend=T, args.legend = list(x="topleft"), main = "Habit")
```


### Simplified

```{r fig.width=9, fig.height=5}
simp_timeIntervention<-factor(NA,levels=c("short contact time", "days to month","> month"),ordered=T)
simp_timeIntervention[as.numeric(extract$Intervention.time.category) %in% c(1,2)] <- "short contact time"
simp_timeIntervention[as.numeric(extract$Intervention.time.category) %in% c(3,4)] <- "days to month"
simp_timeIntervention[as.numeric(extract$Intervention.time.category) == 5] <- "> month"
table(simp_timeIntervention)
tf_outcomes_bigCat<-cbind(
  cognition=tf_outcomes[,"knowledge"]|tf_outcomes[,"awareness"],
  attitude=tf_outcomes[,"emotion"]|tf_outcomes[,"intention"],
  behavior=tf_outcomes[,"action"]|tf_outcomes[,"habit"]
)
concatenateDidItWork <- function(x)
{
  x<-unique(na.omit(x))
  if(length(x)==1){return(x)}
  if(length(x)==0){return(NA)}
  if(length(x)>1){return("Unclear")}
}
didItWork_outcomes_bigCat <- cbind(
  cognition=apply(didItWork_outcomes[,c("knowledge","awareness")],1,concatenateDidItWork),
  attitude=apply(didItWork_outcomes[,c("emotion","intention")],1,concatenateDidItWork),
  behavior=apply(didItWork_outcomes[,c("action","habit")],1,concatenateDidItWork))
tf_outcomes_bigCat_vector<-rep(NA,3*nrow(tf_outcomes_bigCat))
tf_outcomes_bigCat_vector[tf_outcomes_bigCat]<-rep(colnames(tf_outcomes_bigCat),each=nrow(tf_outcomes_bigCat))[tf_outcomes_bigCat]
A<-table(data.frame(
  didItWork=as.vector(didItWork_outcomes_bigCat),
  timeIntervention=rep(simp_timeIntervention,3),
  outcome=factor(tf_outcomes_bigCat_vector,levels=c("cognition","attitude","behavior"))
           )
)
par(mfrow=c(1,3))
YLIM<-c(0,70)
barplot(A[,,1],  xlab = "Cognition", ylim=YLIM, names.arg = c("short contact\ntime", "days to\nmonth","> month"),cex.name=1.1,col=rainbow(3))
PARMAR<-par("mar")
PARMAR[2]<-1
par(mar=PARMAR)
barplot(A[,,2], xlab="Attitude", ylim=YLIM,yaxt="n",names.arg = c("short contact\ntime", "days to\nmonth","> month"),cex.name=1.1,col=rainbow(3))
barplot(A[,,3], legend=T, args.legend = list(cex=1.5, title="Effectiveness"), xlab="Behavior", ylim=YLIM,yaxt="n",names.arg = c("short contact\ntime", "days to\nmonth","> month"),cex.name=1.1, cex.axis=1.5,col=rainbow(3))
```


# Analisis




# SQL style


```{r}

tablify<-function(dfSQL, row, col, content, changeNA=T, valNA=c(row="No information",col="No information"))
{
  if(changeNA)
  {
    dfSQL[is.na(dfSQL[,row]),row]<-valNA["row"]
    dfSQL[is.na(dfSQL[,col]),col]<-valNA["col"]
  }
  res<-matrix(0,nrow=length(unique(dfSQL[,row])),ncol=length(unique(dfSQL[,col])),dimnames=list(unique(dfSQL[,row]),unique(dfSQL[,col])))
  w_SQL<-as.matrix(dfSQL[,c(row,col)])
  colnames(w_SQL)<-c("row","col")
  res[w_SQL]<-dfSQL[,content]
  return(res)
}

tf_outcomeT<-which(tf_outcomes[,1:6],arr.ind=T)
df_outcomeT<-data.frame(
  idRow=rownames(extract)[tf_outcomeT[,1]],
  outcome=factor(colnames(tf_outcomes[,1:6])[tf_outcomeT[,2]]),
  didItWork=factor(didItWork_outcomes[tf_outcomeT])
  )

byRow<-data.frame(
  idRow=rownames(extract),
  id=extract$id,
  ageMin=extract$age_min_stud,
  ageMax=extract$age_max_stud,
  person=extract$codifico,
  population=popTot,
  curri=curExtraCur,
  outIn=extract$`Outdoor/Indoor/Both`,
  pop=pop,
  timeCat=extract$Intervention.time.category,
  TheoFra=extract$`Theoretical.framework.(big.categories)`,
  mitAda=extract$`Final.mitigation/adaptation`,
  controv=ifelse(extract$controv_clean=="Yes","Controversy","No Controversy")
)
byOutcome<-df_outcomeT

require(sqldf)
byOutcomeTot<-na.omit(sqldf(
  "SELECT idRow,id,population,TheoFra,mitAda,controv,outcome,didItWork
  FROM byRow
  LEFT JOIN byOutcome USING (idRow)
  ORDER BY CAST(idRow as int)
  ",drv = "SQLite"))
byRowDIW<-sqldf(
  "SELECT idRow,id,population,TheoFra,mitAda,controv,
    CASE 
      WHEN GROUP_CONCAT(DISTINCT didItWork) LIKE '%,%' THEN 'Unclear'
      ELSE GROUP_CONCAT(DISTINCT didItWork)
    END didItWork
  FROM byRow
  LEFT JOIN byOutcome USING (idRow)
  GROUP BY idRow,population,TheoFra,mitAda,controv
  ORDER BY CAST(idRow as int)",
  drv = "SQLite")
byOutcomeTot<-sqldf(
  "SELECT idRow,id,person,population,pop,ageCat,ageMin,ageMax,timeCat,TheoFra,mitAda,controv,outcome,didItWork,curri,outIn
  FROM byRow
  LEFT JOIN byOutcome USING (idRow)
  JOIN AgeByRow USING (idRow)
  ORDER BY CAST(idRow as int)
  ",drv = "SQLite")

```



```{r}
require(sqldf)
sqldf(
  "SELECT count(DISTINCT id)
  FROM extract"
  )
```
```{r}
sqldf(
  "
  WITH a AS(
  SELECT DISTINCT idRow,outcome
  FROM byOutcomeTot
  )
  SELECT count(*)
  FROM a
  ")
```




```{r}
barplot(tablify(sqldf("SELECT curri,population,count(DISTINCT id) nbPaper FROM byRow GROUP BY curri, population"),"curri","population","nbPaper"),las=2,legend=T)
```

```{r,fig.height=7}
par(mar=c(12,4,1,1))
barplot(tablify(sqldf("SELECT TheoFra,curri,count(DISTINCT id) nbPaper FROM byRow GROUP BY curri, population"),"TheoFra","curri","nbPaper"),las=2,legend=T,col=rainbow(6))
```

## Innovative?

```{r}
sqldf(
  "SELECT count(DISTINCT idRow)
  FROM byRow
  WHERE TheoFra<>'Teacher centered approach' OR outIn <> 'Indoor' OR curri <> 'Curricular'")
sqldf(
  "SELECT count(DISTINCT idRow)
  FROM byRow
  WHERE NOT (TheoFra<>'Teacher centered approach' OR outIn <> 'Indoor' OR curri <> 'Curricular')")
sqldf(
  "SELECT count(DISTINCT id)
  FROM byRow
  WHERE TheoFra='Teacher centered approach' AND outIn = 'Indoor' --AND curri = 'Curricular'")
sqldf(
  "SELECT count(DISTINCT idRow)
  FROM byRow"
)
```

## problem profesor

```{r}
sqldf(
  "SELECT GROUP_CONCAT(id, ', ')
  FROM byRow
  WHERE (TheoFra='Professional development workshop' OR pop IN ('Teachers','Pre-service teachers')) AND curri<> 'Professional development'
  "
)
sqldf(
  "SELECT id,pop,person,TheoFra,curri
  FROM byRow
  WHERE (TheoFra='Professional development workshop' OR pop IN ('Teachers','Pre-service teachers')) AND curri<> 'Professional development'
  "
)

```

```{r}

sqldf(
  "SELECT 
  didItWork,count(*)
  FROM byOutcome
  Group by didItWork
  ")

sqldf(
  "SELECT 
  count(*)
  FROM byOutcome
  ")

```

## Ages and outcomes

```{r}
popAgeSep_df<-sqldf(
  "
  WITH a AS
  (SELECT id, idRow,'4-11' AS agePopCat
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE \"X4.11\" AND pop='Students'
  UNION
  SELECT id, idRow,'12-15'
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE \"X12.15\" AND pop='Students'
  UNION
  SELECT id, idRow, '16-19'
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE \"X16.19\" AND pop='Students'
  UNION
  SELECT id, idRow, 'Teachers'
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE pop='Teachers'
  UNION
  SELECT id, idRow, 'Pre-service teachers'
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE pop='Pre-service teachers'
  UNION
  SELECT id, idRow, 'Parents'
  FROM catAgeConcerned_df
  LEFT JOIN byRow USING (id, idRow)
  WHERE pop='Parents'
  )
  SELECT DISTINCT *
  FROM a
  ORDER BY CAST(idRow AS int)
  "
)
```


```{r}
(tabAgeCatOutomeTot<-tablify(sqldf(
  "SELECT outcome,agePopCat, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  LEFT JOIN popAgeSep_df USING (id, idRow)
  GROUP BY agePopCat,outcome
  "),"outcome","agePopCat","nbPapers")[c("knowledge","awareness","intention","emotion","habit","action","No information"),])
barplot(tabAgeCatOutomeTot,beside=T,col=rainbow(nrow(tabAgeCatOutomeTot)),legend=T)
```



## Effectiveness

```{r fig.height=12}

tabPopTheoFraTot<-tablify(sqldf(
  "SELECT population, TheoFra, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  GROUP BY population,TheoFra
  "),"population","TheoFra","nbPapers")
tabPopTheoFraYes<-tablify(sqldf(
  "SELECT population, TheoFra, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='Yes'
  GROUP BY population,TheoFra
  "),"population","TheoFra","nbPapers")
tabPopTheoFraNo<-tablify(sqldf(
  "SELECT population, TheoFra, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='No'
  GROUP BY population,TheoFra
  "),"population","TheoFra","nbPapers")
tabPopTheoFraUnclear<-tablify(sqldf(
  "SELECT population, TheoFra, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='Unclear'
  GROUP BY population,TheoFra
  "),"population","TheoFra","nbPapers")
colComplete<-unique(c(colnames(tabPopTheoFraYes),colnames(tabPopTheoFraUnclear),colnames(tabPopTheoFraNo)))
rowComplete<-unique(c(rownames(tabPopTheoFraYes),rownames(tabPopTheoFraUnclear),rownames(tabPopTheoFraNo)))
tabPopTheoFraYes_comp<-tabPopTheoFraNo_comp<-tabPopTheoFraUnclear_comp<-matrix(0,nrow=length(rowComplete),ncol=length(colComplete),dimnames=list(rowComplete,colComplete))
for(i in rownames(tabPopTheoFraYes_comp)){
  for(j in colnames(tabPopTheoFraYes_comp)){
    if(i %in% rownames(tabPopTheoFraYes) & j %in% colnames(tabPopTheoFraYes))
    {
      tabPopTheoFraYes_comp[i,j]<-tabPopTheoFraYes[i,j]
    }
    if(i %in% rownames(tabPopTheoFraUnclear) & j %in% colnames(tabPopTheoFraUnclear))
    {
      tabPopTheoFraUnclear_comp[i,j]<-tabPopTheoFraUnclear[i,j]
    }
    if(i %in% rownames(tabPopTheoFraNo) & j %in% colnames(tabPopTheoFraNo))
    {
      tabPopTheoFraNo_comp[i,j]<-tabPopTheoFraNo[i,j]
    }
  }
}
layout.matrix=matrix(1:4,nrow=4)
layout(layout.matrix,heights=c(1,1,1,1.7))
par(mar=c(0,4,4,1))
barplot(t(tabPopTheoFraYes_comp),beside=T,names.arg = rep("",nrow(tabPopTheoFraYes_comp)),col=rainbow(ncol(tabPopTheoFraYes_comp)),main="Yes",ylim=c(0,max(tabPopTheoFraTot)))
barplot(t(tabPopTheoFraNo_comp),beside=T,names.arg = rep("",nrow(tabPopTheoFraYes_comp)),col=rainbow(ncol(tabPopTheoFraYes_comp)),main="No",ylim=c(0,max(tabPopTheoFraTot)),legend=T,args.legend = list(x="topleft"))
barplot(t(tabPopTheoFraUnclear_comp),beside=T,names.arg = rep("",nrow(tabPopTheoFraYes_comp)),col=rainbow(ncol(tabPopTheoFraYes_comp)),main="Unclear",ylim=c(0,max(tabPopTheoFraTot)),las=2)
par(mar=c(12,4,4,1))
barplot(t(tabPopTheoFraTot),beside=T,col=rainbow(ncol(tabPopTheoFraYes_comp)),main="Total",las=2)

```
 
```{r fig.height=12}

tabPopoutcomeTot<-tablify(sqldf(
  "SELECT population, outcome, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  GROUP BY population,outcome
  "),"population","outcome","nbPapers")
tabPopoutcomeYes<-tablify(sqldf(
  "SELECT population, outcome, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='Yes'
  GROUP BY population,outcome
  "),"population","outcome","nbPapers")
tabPopoutcomeNo<-tablify(sqldf(
  "SELECT population, outcome, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='No'
  GROUP BY population,outcome
  "),"population","outcome","nbPapers")
tabPopoutcomeUnclear<-tablify(sqldf(
  "SELECT population, outcome, count(DISTINCT id) nbPapers
  FROM byOutcomeTot
  WHERE didItWork='Unclear'
  GROUP BY population,outcome
  "),"population","outcome","nbPapers")
colComplete<-unique(c(colnames(tabPopoutcomeYes),colnames(tabPopoutcomeUnclear),colnames(tabPopoutcomeNo)))
rowComplete<-unique(c(rownames(tabPopoutcomeYes),rownames(tabPopoutcomeUnclear),rownames(tabPopoutcomeNo)))
tabPopoutcomeYes_comp<-tabPopoutcomeNo_comp<-tabPopoutcomeUnclear_comp<-matrix(0,nrow=length(rowComplete),ncol=length(colComplete),dimnames=list(rowComplete,colComplete))
for(i in rownames(tabPopoutcomeYes_comp)){
  for(j in colnames(tabPopoutcomeYes_comp)){
    if(i %in% rownames(tabPopoutcomeYes) & j %in% colnames(tabPopoutcomeYes))
    {
      tabPopoutcomeYes_comp[i,j]<-tabPopoutcomeYes[i,j]
    }
    if(i %in% rownames(tabPopoutcomeUnclear) & j %in% colnames(tabPopoutcomeUnclear))
    {
      tabPopoutcomeUnclear_comp[i,j]<-tabPopoutcomeUnclear[i,j]
    }
    if(i %in% rownames(tabPopoutcomeNo) & j %in% colnames(tabPopoutcomeNo))
    {
      tabPopoutcomeNo_comp[i,j]<-tabPopoutcomeNo[i,j]
    }
  }
}
layout.matrix=matrix(1:4,nrow=4)
layout(layout.matrix,heights=c(1,1,1,1.7))
par(mar=c(0,4,4,1))
barplot(t(tabPopoutcomeYes_comp),beside=T,names.arg = rep("",nrow(tabPopoutcomeYes_comp)),col=rainbow(ncol(tabPopoutcomeYes_comp)),main="Yes",ylim=c(0,max(tabPopoutcomeTot)))
barplot(t(tabPopoutcomeNo_comp),beside=T,names.arg = rep("",nrow(tabPopoutcomeYes_comp)),col=rainbow(ncol(tabPopoutcomeYes_comp)),main="No",ylim=c(0,max(tabPopoutcomeTot)),legend=T,args.legend = list(x="topleft"))
barplot(t(tabPopoutcomeUnclear_comp),beside=T,names.arg = rep("",nrow(tabPopoutcomeYes_comp)),col=rainbow(ncol(tabPopoutcomeYes_comp)),main="Unclear",ylim=c(0,max(tabPopoutcomeTot)),las=2)
par(mar=c(12,4,4,1))
barplot(t(tabPopoutcomeTot),beside=T,col=rainbow(ncol(tabPopoutcomeYes_comp)),main="Total",las=2)

```

### Young student

```{r}
sqldf(
  "SELECT DISTINCT id,idRow,ageMin,ageMax,population, TheoFra,outcome,didItWork,curri,outIn
  FROM byOutcomeTot
  FULL OUTER JOIN catAgeConcerned_df USING (id,idRow)
  WHERE \"X4.11\" AND population='Students (4-11)'
  ORDER BY outcome
   --CAST(idRow AS int)
  "
)
```
```{r}
sqldf(
  "SELECT outcome,didItWork,count(DISTINCT id), GROUP_CONCAT(DISTINCT id)
  FROM byOutcomeTot
  FULL OUTER JOIN catAgeConcerned_df USING (id,idRow)
  WHERE \"X4.11\" AND population = 'Students (4-11)'
  GROUP BY outcome,didItWork
  ORDER BY outcome
  "
)
```
```{r}
sqldf(
  "SELECT min(ageMin)
  FROM byOutcomeTot
  FULL OUTER JOIN catAgeConcerned_df USING (id,idRow)
  WHERE \"X4.11\" AND population = 'Students (4-11)'
  "
)
```






```{r}
sqldf(
  "SELECT id, idRow, population,ageMin,ageMax, outcome, didItWork
  FROM byOutcomeTot
  FULL OUTER JOIN catAgeConcerned_df USING (id,idRow)
  WHERE id LIKE 'Korfgen%'
  "
)
```

## Ages percentages

Only accounting for students:

```{r}
sqldf(
  "SELECT pop, ageCat, count(DISTINCT id)
  FROM byOutcomeTot
  FULL OUTER JOIN catAgeConcerned_df USING (id,idRow)
  GROUP BY pop, ageCat
  "
)
```


## Outcomes numbers
```{r}
for_outcomeByDoc<- by(tf_outcomes,extract$id,function(x)apply(x,2,any))
outcomeByDoc<-Reduce(rbind,for_outcomeByDoc)
rownames(outcomeByDoc)<-names(for_outcomeByDoc)
colSums(outcomeByDoc)/146
```


# Exploring more (AFD requests)

## Income group

The countries concerned are:

```{r}
tapply(countryDoc,incomeDoc,function(x)sort(table(x),decreasing = T))
```
The studies which are concerned are: 

```{r}
tapply(countryDoc,incomeDoc,function(x)unique(names(x)))
```


### Evolution over time

```{r}
all(names(yearPaper)==names(incomeDoc))
(tbYearIncome<-table(incomeDoc,yearPaper))
barplot(tbYearIncome,col=rainbow(nlevels(incomeDoc)),legend=T, args.legend=list(title="Country income",x="topleft"),las=2)
```

### Comparison with population

```{r}
all(names(populClean)==names(incomeDoc))
(tbPopIncome<-table(populClean,incomeDoc))
barplot(tbPopIncome,col=rainbow(nlevels(populClean)),legend=T,args.legend = list(title="Population"),xlab="Country income",beside=T)
```


### Age of students

Note, it is not based on n=146, because one paper may have more than one age class, and not all papers are on students


```{r}
nrow(catAgeConcerned)==length(incomeDoc[extract$id])
resAgeIncome<-by(catAgeConcerned[populClean=="Students",],incomeDoc[extract$id][populClean=="Students"],colSums)
tbAgeIncome<-as.table(as.matrix(Reduce(rbind,resAgeIncome)))
rownames(tbAgeIncome)<-levels(incomeDoc)
tbAgeIncome<-t(tbAgeIncome)
barplot(tbAgeIncome,beside=T,col=rainbow(nrow(tbAgeIncome)),legend=T,xlab="Country income", args.legend="Student ages")
```

### Rural/Urban

Note n=152 (6 papers with more than two populations)

```{r}
(tbRururbIncome<-table(rururbClean,incomeDoc[extract$id]))
barplot(tbRururbIncome,beside=T,col=rainbow(nrow(tbRururbIncome)),legend=T)
```


### Comparison with controversy

```{r}
all(names(controvByDoc)==names(incomeDoc))
(tbControvIncome<-table(controvByDoc,incomeDoc))
barplot(tbControvIncome,col=c("blue","red"),legend=T,args.legend = list(title="Controversy"),xlab="Country income")
```


### Comparison with mitigation/adaptation

Note n=152

```{r}
(tbMitiadaptIncome <- table(extract$`Final.mitigation/adaptation`,incomeDoc[extract$id]))
barplot(tbMitiadaptIncome,beside=T,col=rainbow(nrow(tbMitiadaptIncome)),legend=T)
```



### Comparison with curricular/extracurricular

Since one study might concern more than one type of curricular/extracurricular, we are for these in the base n=152 instead of n=146

```{r}
kable(tbCurIncome<-table(curExtraCur,incomeDoc[extract$id]))
barplot(tbCurIncome,beside=T,col=rainbow(nlevels(factor(curExtraCur))),legend=T, xlab="Country income")
```


### Comparison with pedagogical tools

n=152

```{r}
(tbPedtoolsIncome<-table(extract$Categories.type.of.intervention,incomeDoc[extract$id]))
barplot(tbPedtoolsIncome,beside=T,col=rainbow(nrow(tbPedtoolsIncome)),legend=T, xlab="Country income")
```

### Comparison with theoretical framework
n=152

```{r}
(tbTheofraIncome<-table(factor(extract$`Theoretical.framework.(big.categories)`,levels=names(sort(table(extract$`Theoretical.framework.(big.categories)`),decreasing=T))),incomeDoc[extract$id]))
barplot(tbTheofraIncome,beside=T,col=rainbow(nrow(tbTheofraIncome)),legend=T, xlab="Country income")
```

### Comparison with time


```{r}
tbTempIncome<-table(extract$Intervention.time.category,incomeDoc[extract$id])
barplot(tbTempIncome,beside=T,col=rainbow(nrow(tbTempIncome)),legend=T, xlab="Country income")
```



### Comparison with outcomes and effectiveness


```{r}
resOutcomeIncome<-by(tf_outcomes,incomeDoc[extract$id],colSums)
tbOutcomeIncome<-as.table(as.matrix(Reduce(rbind,resOutcomeIncome)))
rownames(tbOutcomeIncome)<-levels(incomeDoc)
(tbOutcomeIncome<-t(tbOutcomeIncome))
resOutcomeIncome_No<-by(didItWork_outcomes,incomeDoc[extract$id],function(tab)apply(tab,2,function(x)sum(x=="No",na.rm = T)))
tbOutcomeIncome_No<-as.table(as.matrix(Reduce(rbind,resOutcomeIncome_No)))
rownames(tbOutcomeIncome_No)<-levels(incomeDoc)
(tbOutcomeIncome_No<-t(tbOutcomeIncome_No))
resOutcomeIncome_Unclear<-by(didItWork_outcomes,incomeDoc[extract$id],function(tab)apply(tab,2,function(x)sum(x=="Unclear",na.rm = T)))
tbOutcomeIncome_Unclear<-as.table(as.matrix(Reduce(rbind,resOutcomeIncome_Unclear)))
rownames(tbOutcomeIncome_Unclear)<-levels(incomeDoc)
(tbOutcomeIncome_Unclear<-t(tbOutcomeIncome_Unclear))



bp<-barplot(tbOutcomeIncome,beside=T,col=rainbow(nrow(tbOutcomeIncome)),legend=T,xlab="Country income", args.legend=list(x="top"))
rect(xleft=as.vector(bp)-0.5,ybottom = 0,xright = as.vector(bp)+.5,ytop = as.vector(tbOutcomeIncome_No),density=20,angle = 45)
rect(xleft=as.vector(bp)-0.5,ybottom = as.vector(tbOutcomeIncome_No),xright = as.vector(bp)+.5,ytop = as.vector(tbOutcomeIncome_No)+as.vector(tbOutcomeIncome_Unclear),density=20,angle = 90)
legend("topright",density=c(0,20,20),angle=c(0,45,90),title="Did it work?",c("Yes","No","Unclear"))
```




## Rural/urban

```{r}
rururbDoc<-factor(tapply(as.character(rururbClean),extract$id,unique),levels=c("Urban","Rural","Both","Not given"))
```


### Evolution over time

```{r}
all(names(yearPaper)==names(rururbDoc))
(tbYearRururb<-table(rururbDoc,yearPaper))
barplot(tbYearRururb,col=rainbow(nlevels(rururbDoc)),legend=T, args.legend=list(title="Rural/Urban",x="topleft"),las=2)
```

### Comparison with population

```{r}
all(names(populClean)==names(rururbDoc))
(tbPopRururb<-table(populClean,rururbDoc))
barplot(tbPopRururb,col=rainbow(nlevels(populClean)),legend=T,args.legend = list(title="Population"),xlab="Rural/Urban",beside=T)
```


### Age of students

Note, it is not based on n=146, because one paper may have more than one age class, and not all papers are on students


```{r}
nrow(catAgeConcerned)==length(rururbDoc[extract$id])
resAgeRururb<-by(catAgeConcerned[populClean=="Students",],rururbDoc[extract$id][populClean=="Students"],colSums)
tbAgeRururb<-as.table(as.matrix(Reduce(rbind,resAgeRururb)))
rownames(tbAgeRururb)<-levels(rururbDoc)
tbAgeRururb<-t(tbAgeRururb)
barplot(tbAgeRururb,beside=T,col=rainbow(nrow(tbAgeRururb)),legend=T,xlab="Rural/Urban", args.legend="Student ages")
```

### Comparison with controversy

```{r}
all(names(controvByDoc)==names(rururbDoc))
(tbControvRururb<-table(controvByDoc,rururbDoc))
barplot(tbControvRururb,col=c("blue","red"),legend=T,args.legend = list(title="Controversy"),xlab="Rural/Urban")
```


### Comparison with mitigation/adaptation

Note n=152

```{r}
(tbMitiadaptRururb <- table(extract$`Final.mitigation/adaptation`,rururbDoc[extract$id]))
barplot(tbMitiadaptRururb,beside=T,col=rainbow(nrow(tbMitiadaptRururb)),legend=T)
```



### Comparison with curricular/extracurricular

Since one study might concern more than one type of curricular/extracurricular, we are for these in the base n=152 instead of n=146

```{r}
kable(tbCurRururb<-table(curExtraCur,rururbDoc[extract$id]))
barplot(tbCurRururb,beside=T,col=rainbow(nlevels(factor(curExtraCur))),legend=T, xlab="Rural/Urban")
```


### Comparison with pedagogical tools

n=152

```{r}
(tbPedtoolsRururb<-table(extract$Categories.type.of.intervention,rururbDoc[extract$id]))
barplot(tbPedtoolsRururb,beside=T,col=rainbow(nrow(tbPedtoolsRururb)),legend=T, xlab="Rural/Urban")
```

### Comparison with theoretical framework
n=152

```{r}
(tbTheofraRururb<-table(factor(extract$`Theoretical.framework.(big.categories)`,levels=names(sort(table(extract$`Theoretical.framework.(big.categories)`),decreasing=T))),rururbDoc[extract$id]))
barplot(tbTheofraRururb,beside=T,col=rainbow(nrow(tbTheofraRururb)),legend=T, xlab="Rural/Urban")
```

### Comparison with time


```{r}
tbTempRururb<-table(extract$Intervention.time.category,rururbDoc[extract$id])
barplot(tbTempRururb,beside=T,col=rainbow(nrow(tbTempRururb)),legend=T, xlab="Rural/Urban")
```



### Comparison with outcomes and effectiveness


```{r}
resOutcomeRururb<-by(tf_outcomes,rururbDoc[extract$id],colSums)
tbOutcomeRururb<-as.table(as.matrix(Reduce(rbind,resOutcomeRururb)))
rownames(tbOutcomeRururb)<-levels(rururbDoc)
(tbOutcomeRururb<-t(tbOutcomeRururb))
resOutcomeRururb_No<-by(didItWork_outcomes,rururbDoc[extract$id],function(tab)apply(tab,2,function(x)sum(x=="No",na.rm = T)))
tbOutcomeRururb_No<-as.table(as.matrix(Reduce(rbind,resOutcomeRururb_No)))
rownames(tbOutcomeRururb_No)<-levels(rururbDoc)
(tbOutcomeRururb_No<-t(tbOutcomeRururb_No))
resOutcomeRururb_Unclear<-by(didItWork_outcomes,rururbDoc[extract$id],function(tab)apply(tab,2,function(x)sum(x=="Unclear",na.rm = T)))
tbOutcomeRururb_Unclear<-as.table(as.matrix(Reduce(rbind,resOutcomeRururb_Unclear)))
rownames(tbOutcomeRururb_Unclear)<-levels(rururbDoc)
(tbOutcomeRururb_Unclear<-t(tbOutcomeRururb_Unclear))


bp<-barplot(tbOutcomeRururb,beside=T,col=rainbow(nrow(tbOutcomeRururb)),legend=T,xlab="Rural/Urban", args.legend=list(x="top"))
rect(xleft=as.vector(bp)-0.5,ybottom = 0,xright = as.vector(bp)+.5,ytop = as.vector(tbOutcomeRururb_No),density=20,angle = 45)
rect(xleft=as.vector(bp)-0.5,ybottom = as.vector(tbOutcomeRururb_No),xright = as.vector(bp)+.5,ytop = as.vector(tbOutcomeRururb_No)+as.vector(tbOutcomeRururb_Unclear),density=20,angle = 90)
legend("topright",density=c(0,20,20),angle=c(0,45,90),title="Did it work?",c("Yes","No","Unclear"))
```


## Conclusions: country income and Rural/Urban

| Comparison | Country income | Rural/Urban |
|-----------:|:---------------|:------------|
| Publication years | Low and middle outcome are more important in last years. Middle to low are present in 2015, 2019 and 2022 only | Rural only from 2015, both from 2008, no clear pattern |
| Population | Comparatively more students in high income, only students in low, 1 study only for mixed in middle, parents in high income only | In rural and both very few other populations than students |
| Student age | Not much to say | Very few of the youngest in in Rural, 12-15 and 16-19 comparable in Rural while more 12-15 in urban |
| Rural/Urban | Vey few studies in Rural/Both in middle and low income countries | --- |
| Controversy | Controversy in only high incomes | Comparatively more controversy in rural (probably republican importance in rural USA) |
| Mitigation/adaptation | Adaptation is particularly present in Middle to high income countries (more studies than in high income countries, even though less total studies) | No adaptation in rural!!!, but more both than mitigation, contrary to Urban |
| Curricular/Extracurricular | Professional development comparatively more important in middle, only curricular in low | More extracurricular in rural, contrary to urban |
| Pedagogical tools | Not much to say, due to numbers game-based only in high income, no project-based, technology, cultural and games in low | In rural only lesson based and combined strategies. When both a bit of curriculum based, cultural based and game-based but comparatively less than in urban |
| Theoretical framework | Alternative comparatively much more important in high income countries. Teacher centered comparatively less important in high income countries (more "traditional" way to teach in lower income situations?) | Comparatively more alternative in Rural, learner-centered and teacher-centered and promoting social awareness comparable, contrary to urban  where learner-centered > alternative > teacher centered> professional > promoting social awareness. In both, professional and promoting awareness go before teacher-centered |
| Intervention period | More very short unique and week periods in high income countries, only large periods in low (but missing data) | Very few very short in Rural, but comparatively less large period as well. In both, the main  difference in less week period  |
| Outcomes and effectiveness | Behavior more important in middle to high (comparable to attitudes), no attitude/behavior in low | In rural only cognition/attitudes (no behavior). Cognition and behavior are also more comparable. In both, behavior are more present than attitudes |


